\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage{hyperref}
\usepackage{setspace}

\geometry{margin=0.82in}
\setstretch{1.0}
\setlist[itemize]{topsep=0.2em,itemsep=0.15em,leftmargin=1.3em}
\hypersetup{colorlinks=true, linkcolor=black, urlcolor=blue}
\pagestyle{empty}

\newcommand{\Aether}{\AE{}ther}
\newcommand{\Aflow}{\AE{}ther-flow}
\newcommand{\TheoryName}{\Aflow{} Interpretation of Relativity}

\title{\textbf{External Review Cover Memo}\\[0.35em]
\large Frozen Product-A / Product-B Snapshot}
\author{}
\date{April 17, 2026}

\begin{document}

\maketitle

This memo fixes the external-review snapshot for \emph{The \TheoryName{}}. Product A and Product B are to be reviewed as separate outputs under the publication split already recorded in \emph{Publication Architecture}. Packet C is limited to literature positioning and novelty discipline. No packet is asking a reviewer to bless a reopened derivational line, and any derivation restart remains blocked unless a new-line charter can already be written concretely as equations rather than prose.

\section*{Claims In Scope}
\begin{itemize}
    \item \textbf{Product A:} the benchmark package is a positive exact-GR theory statement already in hand. It adopts one operative metric, universal matter coupling, and ordinary relativistic observer law exactly, while using \Aether{} / \Aflow{} language as disciplined ontology and interpretation.
    \item \textbf{Product B:} on the current frozen primitive-reservoir bridge object, the benchmark package is \emph{not} derived. The scoped verdict is \texttt{Not Derived On Current Line}; the claim is line-specific and structural, not universal.
    \item \textbf{Packet C:} the project should be judged for honest literature placement as an exact-GR interpretive package together with an open emergent / reconstruction / induced-gravity research program.
\end{itemize}

\section*{Claims Not In Scope}
\begin{itemize}
    \item no completed first-principles substrate derivation of GR is being claimed
    \item no low-energy non-GR alternative gravity sector is being claimed
    \item no universal impossibility theorem against every future \Aether{} / \Aflow{} completion is being claimed
    \item no same-output deeper relay below the frozen bridge object is being treated as current progress
\end{itemize}

\section*{Requested Review Split}
\begin{itemize}
    \item \textbf{Packet A:} send to a GR / foundations reader to test Product A for coherence, claim-boundary honesty, and real-but-narrow novelty.
    \item \textbf{Packet B:} send to a mathematical physicist to test whether the frozen-line obstruction really earns \texttt{Not Derived On Current Line}.
    \item \textbf{Packet C:} send to an emergence / reconstruction / literature reader to test category placement, missing citations, and novelty discipline.
\end{itemize}

\section*{Hold Rule}
Until outside review returns, the repository should either circulate the benchmark package and bounded no-go as frozen outputs or remain silent about renewed derivation. The only exception is a genuinely new line that can already complete the new-line charter concretely at the level of equations, local maps, metric generation, mode control, relativistic recovery, and verdict conditions.

\end{document}
