\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{geometry}
\usepackage{amsmath,amssymb,amsfonts,amsthm,mathtools}
\usepackage{bm}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{booktabs}
\usepackage{array}
\usepackage{setspace}
\usepackage{mathrsfs}
\usepackage{physics}

\geometry{margin=1in}
\hypersetup{colorlinks=true, linkcolor=black, urlcolor=blue, citecolor=black}
\setlist[enumerate]{topsep=0.4em,itemsep=0.35em}
\setlist[itemize]{topsep=0.3em,itemsep=0.25em}
\titleformat{\section}{\large\bfseries}{\thesection.}{0.5em}{}
\titleformat{\subsection}{\normalsize\bfseries}{\thesubsection.}{0.5em}{}
\setstretch{1.06}

\newcommand{\Aether}{\AE{}ther}
\newcommand{\Aflow}{\AE{}ther-flow}
\newcommand{\TheoryName}{\Aflow{} Interpretation of Relativity}
\newcommand{\TheoryProgram}{\Aether{} / \Aflow{} framework}
\newcommand{\CompletedMetric}{g^{\sharp}}

\newcommand{\LiftSelectionPackage}{\mathfrak L^{\mathrm{disp,body,sel}}}
\newcommand{\VisibleBodyForcingLaw}{\mathscr F^{\mathrm{disp,resp,vis,body}}}
\newcommand{\VisibleResponseOperator}{S^{\mathrm{disp,resp,vis}}}
\newcommand{\MinimalReducedStructure}{\mathfrak S^{\mathrm{disp,resp,red,min}}}
\newcommand{\CurrentBodyImageCore}{\mathfrak S^{\mathrm{disp,resp,cbimg}}}

\newtheorem{definition}{Definition}
\newtheorem{proposition}{Proposition}
\newtheorem{remark}{Remark}
\newtheorem{corollary}{Corollary}
\newtheorem{theorem}{Theorem}

\title{\textbf{The \TheoryName{}}\\[0.4em]
\large Primitive-Reservoir Observer-Reduction\\
\large Section-Centered Hidden-Response\\
\large Displacement-Body Quadratic Forcing Law\\
\large from Body-Lift Response Selection\\
\large Next Benchmark Criterion}
\author{}
\date{}

\begin{document}

\maketitle

\begin{abstract}
The current active-primary theorem now proves that the section-centered displacement-body quadratic forcing law \(\VisibleBodyForcingLaw\) is itself already derived canonically from a smaller explicit body-lift response selection \(\LiftSelectionPackage\) on the fixed displacement body. The current visible-response operator family \(\VisibleResponseOperator\) and canonical minimal visible-response representative \(\MinimalReducedStructure\) are therefore downstream consequences of that same smaller package rather than separately primitive data.

This note records the routing consequence of that gain. The next honest benchmark-facing move must now derive or justify the current body-lift response selection \(\LiftSelectionPackage\) itself from still more primitive explicit substrate structure while preserving the same benchmark one-metric package, the same ordinary matter route, and the same claim boundary. Another manuscript that merely restates the same selected-lift package, merely reproduces the same body-level forcing law \(\VisibleBodyForcingLaw\), merely re-extends it to the same visible-response operator family \(\VisibleResponseOperator\), merely re-presents the same canonical minimal visible-response representative \(\MinimalReducedStructure\), or restores the full canonical current-body image core \(\CurrentBodyImageCore\) or any other larger same-output package does not count as the clean next step. The one operative metric remains exactly \(\CompletedMetric\), there is no second operative metric, the low-energy matter law is not enlarged, and no stronger promotion language is licensed.
\end{abstract}

\section{Introduction}

The active derivational program of \TheoryName{} is now one layer sharper again below the displacement-body forcing-law frontier. The new theorem shows that even the current body-level forcing law is no longer primitive once the smaller body-lift response selection is fixed. The benchmark-facing datum has therefore moved below the body-law presentation itself.

The present note records the routing consequence of that gain. It does not reopen the body-law presentation, the operator-family presentation, the canonical minimal visible-response representative, the full canonical current-body image core, the larger reduced-carrier presentation, the older projection/body presentation, or the full displacement-response substrate-law presentation as if any of those were again the live burden. It records only which kind of next manuscript would now count as an honest benchmark-facing gain below the new selected-lift frontier.

\paragraph{Framework and claim boundary.}
\TheoryProgram{} denotes the broader \Aether{} / \Aflow{} framework built on the claims that the \Aether{} is the underlying four-dimensional substrate of reality, the \Aflow{} is its intrinsic ordered motion, observed three-dimensional space is the local experiential slice of that deeper substrate, S-time is the experienced order of change arising from matter, light, and the \Aflow{}, and observed expansion is the three-dimensional appearance of deeper four-dimensional ordered motion. Within that framework, \TheoryName{} denotes the exact-closure theory in which the effective gravitational dynamics are adopted to be exactly Einsteinian with universal matter coupling. In the active sequence, \emph{adoption} means use of that established relativistic dynamics without claiming substrate derivation, while \emph{derivation} is reserved for a first-principles recovery from explicit substrate variables.

The present note stays strictly inside that boundary. It records only which kind of next manuscript would now count as an honest benchmark-facing gain below the body-lift response-selection frontier.

\section{Fixed Inputs}

\begin{definition}[Current body-lift response-selection frontier inputs]
The criterion recorded here uses the following fixed inputs.
\begin{enumerate}
    \item The benchmark exact-closure package, which fixes the public one-metric GR target of the repository.
    \item The benchmark gatekeeping layer, including the recorded safeguard that blocks same-output deeper-origin relays from counting as new front-line progress once the live benchmark-relevant datum is unchanged.
    \item The preserved theorem chain showing that the older projection/body and current-image-core presentations already collapse benchmark-facingly to the canonical minimal visible-response representative, that the visible-response representative itself already follows from the smaller body-level forcing law \(\VisibleBodyForcingLaw\), and now that even that current forcing law already follows from the smaller body-lift response selection \(\LiftSelectionPackage\).
    \item The recorded fact that the current body-response core and all currently recorded downstream benchmark-facing consequences already factor through the same forcing law \(\VisibleBodyForcingLaw\), and therefore now through the smaller selected-lift package \(\LiftSelectionPackage\).
\end{enumerate}
\end{definition}

\begin{remark}
The present note does not replace those manuscripts. It records the routing consequence of reading them together under the active safeguard against recursive depth drift.
\end{remark}

\section{Why the Live Burden Now Sits Below Body-Law Restatement}

\begin{proposition}[The live burden is renewed below body-law restatement]
At the current stage of the primitive-reservoir observer-reduction line, the body-lift response-selection theorem renews the live benchmark-facing burden below any mere restatement of the same body-lift response selection \(\LiftSelectionPackage\), the same section-centered displacement-body quadratic forcing law \(\VisibleBodyForcingLaw\), the same visible-response operator family \(\VisibleResponseOperator\), or the same canonical minimal visible-response representative \(\MinimalReducedStructure\).
\end{proposition}

\begin{proof}
That theorem changes benchmark-facing status because it proves that the current body-level forcing law is not primitive once the smaller selected-lift package is fixed. A later manuscript that merely rewrites the same selected-lift package, merely rewrites the same body-level law, merely recovers the same operator family from it again, or merely restates the same canonical minimal visible-response representative removes no remaining benchmark-facing freedom. The live burden therefore no longer sits on another body-law replay. It sits on deriving or justifying the selected-lift package itself from still more primitive explicit substrate structure.
\end{proof}

\begin{definition}[Benchmark-neutral same-selection relay below the current frontier]
A \emph{benchmark-neutral same-selection relay below the current frontier} is a manuscript that preserves the same benchmark one-metric output, the same ordinary matter route, the same fixed displacement body, the same body-lift response selection \(\LiftSelectionPackage\), the same section-centered displacement-body quadratic forcing law \(\VisibleBodyForcingLaw\), the same visible-response operator family \(\VisibleResponseOperator\), the same canonical minimal visible-response representative \(\MinimalReducedStructure\), and the same downstream benchmark-facing consequences while merely restating that same selected-lift package, merely replaying the same body-level law, merely replaying its operator extension, merely rewriting the same representative, restoring the already-spent full current-image-core package \(\CurrentBodyImageCore\), re-expanding to a larger reduced-carrier presentation, restoring the older projection/body presentation, replaying the full displacement-response substrate law, or otherwise carrying the same visible-response datum through another larger same-output realization.
\end{definition}

\section{The Current Post-Selection Criterion}

\begin{definition}[Admissible next benchmark-facing manuscript below the current frontier]
Below the current body-lift response-selection frontier, a manuscript counts as an admissible next benchmark-facing move only if it does at least one of the following:
\begin{enumerate}
    \item derives or justifies the current selected body-lift response package \(\LiftSelectionPackage\) itself from still more primitive explicit substrate structure;
    \item equivalently derives that current selected-lift package as a canonical readout, minimization law, selection law, or forcing consequence of a still smaller explicit substrate package while preserving the same benchmark one-metric package, the same ordinary matter route, and the same claim boundary;
    \item does one of the previous two without merely replaying the same body-level forcing law \(\VisibleBodyForcingLaw\), the same visible-response operator family \(\VisibleResponseOperator\), or the same canonical minimal visible-response representative \(\MinimalReducedStructure\), and without restoring the full current-image-core package \(\CurrentBodyImageCore\), a larger reduced-carrier presentation, the older projection/body presentation, or the full displacement-response substrate-law presentation.
\end{enumerate}
\end{definition}

\begin{theorem}[Next honest benchmark-facing task below the current frontier]
The next honest benchmark-facing manuscript below the current body-lift response-selection frontier must derive or justify the current selected body-lift response package \(\LiftSelectionPackage\) itself from still more primitive explicit substrate structure. A manuscript that only repeats the same selected-lift package, only re-reads off the same body-level law \(\VisibleBodyForcingLaw\), only re-extends it to the same visible-response operator family \(\VisibleResponseOperator\), only re-presents the same canonical minimal visible-response representative \(\MinimalReducedStructure\), or only restores a larger same-output package does not satisfy the criterion.
\end{theorem}

\begin{proof}
By the preceding proposition, the live burden already lies below any mere restatement of the same selected-lift package or of the same body-law or operator-level presentation that follows from it. The current theorem has spent the option of treating the body-level forcing law as primitive. Therefore a subsequent manuscript must improve on the selected-lift package itself rather than merely accompany it through another representation. A deeper-origin manuscript can do so only if it derives or justifies that current package from still more primitive explicit substrate structure. The remaining honest alternatives are therefore exactly those stated in the definition.
\end{proof}

\section{What the Next Move Should Not Be}

\begin{proposition}[Screened next moves below the current frontier]
Below the current body-lift response-selection frontier, none of the following is the default next benchmark-facing move:
\begin{enumerate}
    \item another same-output relay that merely preserves the current body-lift response selection \(\LiftSelectionPackage\) and therefore merely reproduces the same section-centered displacement-body quadratic forcing law \(\VisibleBodyForcingLaw\), the same visible-response operator family \(\VisibleResponseOperator\), the same canonical minimal visible-response representative \(\MinimalReducedStructure\), the same current body-response core, and the same downstream benchmark-facing consequences;
    \item another manuscript that merely rebuilds the body-level forcing law from the same selected-lift package without deriving that package itself;
    \item another restoration of the full current-image-core package \(\CurrentBodyImageCore\), of a larger reduced-carrier presentation, of the older projection/body presentation, or of the full displacement-response substrate law as if those already-spent larger packages were again the honest current burden;
    \item a manuscript that introduces a second operative metric, enlarges the ordinary matter law, or uses stronger promotion language.
\end{enumerate}
\end{proposition}

\begin{proof}
Items (1) and (2) fail the preceding criterion because they leave the renewed live burden unchanged. Item (3) fails because it returns to larger already-spent same-output packages rather than deriving the selected-lift package itself. Item (4) violates the fixed claim boundary of the benchmark package and therefore cannot count as a disciplined next step on the active line.
\end{proof}

\begin{remark}
This screening statement is not a denial that those deeper or alternative manuscripts may matter strategically. It is a routing statement: they are not the default way to spend the next benchmark-facing move below the current frontier unless they do the same benchmark-facing work named above.
\end{remark}

\section{Conclusion}

The positive result of this note is routing discipline below the body-lift response-selection frontier. The new theorem remains the live benchmark-facing gain because it already proves that the current section-centered displacement-body quadratic forcing law is a canonical consequence of the smaller selected-lift package, and the earlier forcing-law theorem remains preserved handoff history because it first removed the operator-family presentation as the primitive stopping point before the present theorem spent the body-law presentation itself.

The scope remains narrow and honest. The benchmark package is unchanged: the one operative metric is still exactly \(\CompletedMetric\), the ordinary matter route is unchanged, there is no second operative metric, and the low-energy matter law is not enlarged. Nothing here upgrades adoption to derivation or licenses stronger promotion language.

The next open burden is therefore clear. The next benchmark-facing manuscript should derive or justify the current body-lift response selection \(\LiftSelectionPackage\) itself from still more primitive explicit substrate structure. Another same-selection relay, another same body-law restatement, another same operator-extension relay, another same visible-response restatement, another restored current-image-core package, another larger reduced-carrier replay, another restored projection/body presentation, or another replay of the full displacement-response substrate law is not the clean next manuscript target at current scope.

\end{document}
