\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{geometry}
\usepackage{amsmath,amssymb,amsfonts,amsthm,mathtools}
\usepackage{bm}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{booktabs}
\usepackage{array}
\usepackage{setspace}
\usepackage{mathrsfs}
\usepackage{physics}

\geometry{margin=1in}
\hypersetup{colorlinks=true, linkcolor=black, urlcolor=blue, citecolor=black}
\setlist[enumerate]{topsep=0.4em,itemsep=0.35em}
\setlist[itemize]{topsep=0.3em,itemsep=0.25em}
\titleformat{\section}{\large\bfseries}{\thesection.}{0.5em}{}
\titleformat{\subsection}{\normalsize\bfseries}{\thesubsection.}{0.5em}{}
\setstretch{1.06}

\newcommand{\Aether}{\AE{}ther}
\newcommand{\Aflow}{\AE{}ther-flow}
\newcommand{\TheoryName}{\Aflow{} Interpretation of Relativity}
\newcommand{\TheoryProgram}{\Aether{} / \Aflow{} framework}
\newcommand{\CompletedMetric}{g^{\sharp}}
\newcommand{\NanoSectionPackage}{\mathfrak X^{\mathrm{nanosec}}}
\newcommand{\PicoSectionPackage}{\mathfrak Y^{\mathrm{picosec}}}

\newtheorem{definition}{Definition}
\newtheorem{proposition}{Proposition}
\newtheorem{remark}{Remark}
\newtheorem{corollary}{Corollary}
\newtheorem{theorem}{Theorem}

\title{\textbf{The \TheoryName{}}\\[0.4em]
\large Primitive-Reservoir Observer-Reduction\\
\large Nano-Section-Generating Substrate Pico-Section Dynamics\\
\large Next Benchmark Criterion}
\author{}
\date{}

\begin{document}

\maketitle

\begin{abstract}
The active primitive-reservoir observer-reduction line has now moved below the micro-section-generating substrate nano-section dynamics package itself. The earlier nano-section theorem already removed the current nano-section package \(\NanoSectionPackage\) as the primitive stopping point by deriving it canonically from a deeper nano-section-generating substrate pico-section dynamics package \(\PicoSectionPackage\).

This note records the routing consequence of that theorem. Another same-output deeper-origin relay that merely preserves the current pico-section package \(\PicoSectionPackage\) and therefore merely reproduces the same current nano-section package \(\NanoSectionPackage\), together with the same current micro-section and sub-section packages downstream of it, no longer counts as the honest default next benchmark-facing manuscript. Neither does a reopening of the larger transport-image, sub-pre-core, or pre-core packages as if they were again independently live, and neither does a quantum branch that does not do the same benchmark-facing work.

The next honest benchmark-facing move must therefore either derive or justify the deeper pico-section package \(\PicoSectionPackage\) from still more primitive substrate structure in a way that changes benchmark-facing status, or prove a genuinely smaller theorem-level collapse strictly inside that deeper package. The benchmark boundary remains fixed throughout. The one operative metric is still exactly \(\CompletedMetric\), the ordinary matter route is unchanged, there is no second operative metric, the low-energy matter law is not enlarged, and no stronger promotion language is licensed. The positive result of this note is therefore routing discipline at the current pico-section frontier.
\end{abstract}

\section{Introduction}

The active derivational program of \TheoryName{} is no longer at a stage where the micro-section-generating substrate nano-section dynamics package should be treated as the default unexplained stopping point. The earlier nano-section theorem already showed that the current nano-section package \(\NanoSectionPackage\) is canonically generated by a deeper pico-section package \(\PicoSectionPackage\). That theorem therefore spent the derivational option that was still open below the former nano-section frontier.

The present note records the routing consequence of that deeper theorem. It does not reopen the pico-section mathematics, and it does not claim a completed first-principles substrate derivation of gravity. It records only which kind of next manuscript would now count as an honest benchmark-facing gain at the current pico-section frontier.

\paragraph{Framework and claim boundary.}
\TheoryProgram{} denotes the broader \Aether{} / \Aflow{} framework built on the claims that the \Aether{} is the underlying four-dimensional substrate of reality, the \Aflow{} is its intrinsic ordered motion, observed three-dimensional space is the local experiential slice of that deeper substrate, S-time is the experienced order of change arising from matter, light, and the \Aflow{}, and observed expansion is the three-dimensional appearance of deeper four-dimensional ordered motion. Within that framework, \TheoryName{} denotes the exact-closure theory in which the effective gravitational dynamics are adopted to be exactly Einsteinian with universal matter coupling. In the active sequence, \emph{adoption} means use of that established relativistic dynamics without claiming substrate derivation, while \emph{derivation} is reserved for a first-principles recovery from explicit substrate variables.

The present note stays strictly inside that boundary. It records only which kind of next manuscript would now count as an honest benchmark-facing gain at the current pico-section frontier.

\section{Fixed Inputs}

\begin{definition}[Pico-section frontier inputs]
The criterion recorded here uses the following fixed inputs.
\begin{enumerate}
    \item The benchmark exact-closure package, which fixes the public one-metric GR target of the repository.
    \item The benchmark gatekeeping layer, including the recorded safeguard that blocks same-output deeper-origin relays from counting as new front-line progress once the live benchmark-relevant datum is unchanged.
    \item The theorem deriving the current micro-section package from micro-section-generating substrate nano-section dynamics, which had already moved the live burden below the current micro-section package.
    \item The later pico-section theorem, which proves that the current nano-section package \(\NanoSectionPackage\) itself is canonically generated by the deeper nano-section-generating substrate pico-section dynamics package \(\PicoSectionPackage\).
\end{enumerate}
\end{definition}

\begin{remark}
The present note does not replace those manuscripts. It records the routing consequence of reading them together under the active safeguard against recursive depth drift.
\end{remark}

\section{Why the Pico-Section Theorem Is the Frontier}

\begin{definition}[Benchmark-neutral deeper relay at pico-section scope]
A \emph{benchmark-neutral deeper relay at pico-section scope} is a manuscript that preserves the same benchmark one-metric output, the same ordinary matter route, the same current nano-section package \(\NanoSectionPackage\), and the same deeper pico-section package \(\PicoSectionPackage\) while merely relocating the unexplained substrate layer deeper, restating the larger transport-image, sub-pre-core, or pre-core presentations, or repackaging the same pico-section package without a new compression, necessity, uniqueness, or comparably sharp routing gain.
\end{definition}

\begin{proposition}[The pico-section theorem is the live frontier]
At the current stage of the primitive-reservoir observer-reduction line, the theorem deriving the micro-section-generating substrate nano-section dynamics from nano-section-generating substrate pico-section dynamics remains the live benchmark-facing frontier.
\end{proposition}

\begin{proof}
That theorem changes benchmark-facing status at current scope because it removes the current nano-section package \(\NanoSectionPackage\) itself as the unexplained stopping point. The live burden now lies at the deeper pico-section dynamics package \(\PicoSectionPackage\), not at the previously exposed nano-section package. By contrast, a later manuscript that preserves the same benchmark package, the same current nano-section package, and the same deeper pico-section package while merely moving the unexplained layer deeper does not alter benchmark-facing status unless it adds a comparably sharp gain. Therefore the live frontier is now the pico-section theorem rather than the earlier nano-section theorem or any later same-output relay that leaves the deeper pico package unchanged.
\end{proof}

\begin{corollary}[Status of the prior nano-section theorem]
The theorem deriving the current micro-section package from micro-section-generating substrate nano-section dynamics remains preserved benchmark-facing main-line history, but under the current routing safeguard it is no longer by itself the default current frontier.
\end{corollary}

\begin{proof}
That theorem matters because it proved that the current micro-section package is no longer the live stopping point and that the active burden moved to the current nano-section package. But the later pico-section theorem shows that even \(\NanoSectionPackage\) is no longer the present unexplained stopping point. The earlier theorem is preserved history and handoff, while the later theorem defines the current frontier.
\end{proof}

\section{The Next Benchmark Criterion}

\begin{definition}[Admissible next benchmark-facing manuscript at pico-section scope]
At the current pico-section frontier, a manuscript counts as an admissible next benchmark-facing move only if it does at least one of the following:
\begin{enumerate}
    \item derives or justifies the nano-section-generating substrate pico-section dynamics package \(\PicoSectionPackage\) from still more primitive substrate structure in a way that does more than merely relocate the unexplained layer deeper;
    \item proves a genuinely smaller theorem-level collapse strictly inside \(\PicoSectionPackage\);
    \item does either of the previous two while preserving the same benchmark one-metric package, the same ordinary matter route, and the same claim boundary.
\end{enumerate}
\end{definition}

\begin{theorem}[Next honest benchmark-facing task at pico-section scope]
The next honest benchmark-facing manuscript below the current pico-section frontier must either derive or justify the nano-section-generating substrate pico-section dynamics from still more primitive substrate structure in a benchmark-relevant way, or else prove a genuinely smaller collapse strictly inside that deeper package. A manuscript that only repeats the same current nano-section package through another deeper relay, re-expands the discussion back to the larger transport-image, sub-pre-core, or pre-core packages without such a new gain, or invokes a quantum branch without doing the same benchmark-facing work does not satisfy the criterion.
\end{theorem}

\begin{proof}
By Proposition 1, the live frontier already lies at the deeper pico-section package \(\PicoSectionPackage\) rather than at the current nano-section package \(\NanoSectionPackage\) or the larger screened packages. Therefore a subsequent manuscript must improve on that status rather than merely accompany it. A deeper-origin manuscript can do so only if it changes benchmark-facing status by more than depth alone. If it simply reproduces the same current nano-section package through another relay, or merely re-expands the already-screened larger packages, the routing rule classifies it as benchmark neutral. If it invokes an explicitly quantum package without deriving the same deeper pico-section dynamics, collapsing them further, or closing a benchmark derivation gate, it likewise leaves the live burden unchanged. The remaining honest alternatives are therefore exactly those stated in the definition: either a more primitive derivation or justification of the pico-section package itself, or a sharper internal collapse of that package.
\end{proof}

\section{What the Next Move Should Not Be}

\begin{proposition}[Screened next moves]
At the current pico-section frontier, none of the following is the default next benchmark-facing move:
\begin{enumerate}
    \item another same-output deeper-origin relay that merely preserves the current pico-section package \(\PicoSectionPackage\) and therefore merely reproduces the same current nano-section package \(\NanoSectionPackage\) together with the same current micro-section and sub-section packages downstream of it;
    \item another re-expansion back to the larger transport-image, full sub-pre-core, or already-screened pre-core presentations as if they were again independently live burdens;
    \item a quantum branch that does not derive or justify the same deeper pico-section dynamics, collapse them further, or close a benchmark derivation gate in a genuinely new way;
    \item a manuscript that introduces a second operative metric, enlarges the ordinary matter law, or uses stronger promotion language.
\end{enumerate}
\end{proposition}

\begin{proof}
Items (1) and (2) fail the preceding criterion because they do not directly address the current pico-section-level burden. They revisit a same-output relay or a previously screened larger presentation rather than removing the remaining freedom in \(\PicoSectionPackage\) or proving a smaller internal datum there. Item (3) likewise does not directly address the live burden at current scope. It changes vocabulary without changing the benchmark-facing task unless it derives the same deeper package, sharpens it internally, or settles a derivation gate. Item (4) violates the fixed claim boundary of the benchmark package and therefore cannot count as a disciplined next step on the active line. The benchmark package remains the exact one-metric GR package already fixed by adoption, so any admissible next manuscript must preserve that boundary.
\end{proof}

\begin{remark}
This screening statement is not a denial that those deeper or alternative manuscripts may matter strategically. It is a routing statement: they are not the default way to spend the next benchmark-facing move from the current pico-section frontier unless they do the same benchmark-facing work named above.
\end{remark}

\section{Conclusion}

The positive result of this note is routing discipline at the current pico-section frontier. The pico-section theorem remains the live benchmark-facing gain because it already removes the current nano-section package as the unexplained stopping point on the active line. The earlier nano-section theorem remains preserved main-line history, but under the recursive-depth safeguard it is no longer itself the default current frontier.

The scope remains narrow and honest. The benchmark package is unchanged: the one operative metric is still exactly \(\CompletedMetric\), the ordinary matter route is unchanged, there is no second operative metric, and the low-energy matter law is not enlarged. Nothing here upgrades adoption to derivation or licenses stronger promotion language.

The next open burden is therefore clear. The next benchmark-facing manuscript should derive or justify the nano-section-generating substrate pico-section dynamics from still more primitive substrate structure in a way that changes benchmark-facing status, unless the sharper honest gain available instead is a genuinely smaller theorem-level collapse strictly inside that deeper package. Another same-output deeper relay that merely preserves the current pico-section package, a reopening of the larger screened packages, or a quantum branch that does not do that same benchmark-facing work is not the clean next manuscript target at current scope.

\end{document}
