\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{geometry}
\usepackage{amsmath,amssymb,amsfonts,amsthm,mathtools}
\usepackage{bm}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{booktabs}
\usepackage{array}
\usepackage{setspace}
\usepackage{mathrsfs}
\usepackage{physics}

\geometry{margin=1in}
\hypersetup{colorlinks=true, linkcolor=black, urlcolor=blue, citecolor=black}
\setlist[enumerate]{topsep=0.4em,itemsep=0.35em}
\setlist[itemize]{topsep=0.3em,itemsep=0.25em}
\titleformat{\section}{\large\bfseries}{\thesection.}{0.5em}{}
\titleformat{\subsection}{\normalsize\bfseries}{\thesubsection.}{0.5em}{}
\setstretch{1.06}

\newcommand{\Aether}{\AE{}ther}
\newcommand{\Aflow}{\AE{}ther-flow}
\newcommand{\TheoryName}{\Aflow{} Interpretation of Relativity}
\newcommand{\TheoryProgram}{\Aether{} / \Aflow{} framework}

\newcommand{\CompletedMetric}{g^{\sharp}}
\newcommand{\MatterSpace}{\Psi}

\newcommand{\Car}{\mathrm{car}}
\newcommand{\Cur}{\mathrm{cur}}
\newcommand{\Hom}{\mathrm{hom}}

\newcommand{\ForSpace}[1]{\mathcal I_{#1}^{\mathrm{for}}}
\newcommand{\PrimShell}{\mathcal S_{\mathrm{prim}}}
\newcommand{\MetricOut}{\mathscr G_{\mathrm{out}}}
\newcommand{\MatterOut}{\mathscr T_{\mathrm{out}}}

\newcommand{\ProtoSectionBody}[1]{\mathcal B_{#1}^{\mathrm{psec}}}
\newcommand{\ProtoSectionShell}[1]{\mathcal Z_{#1}^{\mathrm{psec}}}
\newcommand{\PrePreProtoSectionVertical}[1]{V_{#1}^{\mathrm{pppresec}}}
\newcommand{\PrePreProtoSectionResidualBody}[1]{\mathcal D_{#1}^{\mathrm{pppresec}}}

\newcommand{\PullbackBodyResponseCore}{\mathfrak S^{\mathrm{sub,proto,pppresec,pb,bodyresp}}}
\newcommand{\PullbackBodyOperatorCore}{\mathfrak S^{\mathrm{sub,proto,pppresec,pb,bodyop}}}
\newcommand{\PullbackOperatorCore}{\mathfrak S^{\mathrm{sub,proto,pppresec,pb,op}}}
\newcommand{\PrePreProtoSectionPullbackCore}{\mathfrak S^{\mathrm{sub,proto,pppresec,pb}}}
\newcommand{\PreProtoSectionResidualPackage}{\mathfrak R^{\mathrm{sub,proto,presec,res}}}
\newcommand{\PreProtoSectionPackage}{\mathfrak R^{\mathrm{sub,proto,presec}}}
\newcommand{\PreProtoSectionMinSectionCore}{\mathfrak R^{\mathrm{sub,proto,presec,sec}}}

\newcommand{\VisibleBodyForcingLaw}[1]{\mathscr F_{#1}^{\mathrm{disp,resp,vis,body}}}
\newcommand{\VisibleResponseOperator}[1]{S_{#1}^{\mathrm{disp,resp,vis}}}
\newcommand{\MinimalReducedStructure}{\mathfrak S^{\mathrm{disp,resp,red,min}}}

\newcommand{\LiftSelectionCarrier}[1]{\mathcal U_{#1}^{\mathrm{disp,body,sel}}}
\newcommand{\SelectedResponseLift}[1]{\Lambda_{#1}^{\mathrm{disp,body,sel}}}
\newcommand{\SelectedResponseOperator}[1]{K_{#1}^{\mathrm{disp,body,sel}}}

\newtheorem{definition}{Definition}
\newtheorem{proposition}{Proposition}
\newtheorem{remark}{Remark}
\newtheorem{corollary}{Corollary}
\newtheorem{theorem}{Theorem}

\title{\textbf{The \TheoryName{}}\\[0.4em]
\large Primitive-Reservoir Observer-Reduction\\
\large Section-Centered Hidden-Response\\
\large Displacement-Body Quadratic Forcing Law\\
\large from Body-Lift Response Selection}
\author{}
\date{}

\begin{document}

\maketitle

\begin{abstract}
The current active-primary theorem already proves that the canonical minimal visible-response representative \(\MinimalReducedStructure\) and its visible-response operator family are canonical consequences of a smaller section-centered displacement-body quadratic forcing law on the fixed displacement body. The next honest benchmark-facing move is therefore no longer another same-body-law restatement, another same operator-extension relay, or another restored larger same-output package. It is to derive that current body-level forcing law itself from still more primitive explicit substrate structure.

The present note makes that move in the smallest explicit package presently available below the forcing-law frontier. For each sector it introduces a benchmark-faithful body-lift response selection: the fixed proto-section benchmark base and fixed section-centered displacement body together with a finite-dimensional selected substrate carrier, a smooth linear selected response lift over the displacement fibers, and a smooth positive self-adjoint selected response operator. The current displacement-body quadratic forcing law is then the selected substrate-response energy of the chosen response-carrying lift on the actual displacement body. Hence the current body-level forcing law is no longer primitive once this smaller explicit body-lift response selection is fixed.

The benchmark boundary remains unchanged throughout. The one operative metric is still exactly \(\CompletedMetric\), the ordinary matter route is unchanged, there is no second operative metric, the low-energy matter law is not enlarged, and no stronger promotion language is licensed. By the previous forcing-law theorem, the same canonical minimal visible-response representative, the same current body-response core, and every currently recorded downstream benchmark-facing consequence then follow unchanged. The remaining honest burden therefore moves below the current body-level forcing law to a deeper derivation or justification of the selected body-lift response package itself rather than another same-output replay.
\end{abstract}

\section{Introduction}

The active derivational program of \TheoryName{} has now spent the presentational freedom inside the current visible-response datum and, after that, the presentational freedom inside the current body-level forcing law itself. The visible-response operator family and canonical minimal visible-response representative are no longer primitive once the smaller section-centered displacement-body quadratic forcing law is fixed. The next honest question is therefore narrower again: what smaller explicit substrate structure forces that current body-level law?

The present note takes the smallest clean route currently available below the forcing-law frontier. It does not restore the full displacement-response substrate law, the larger projection/body presentation, the full canonical current-body image core, or any other larger same-output package as if those were again the live benchmark-facing datum. Instead it retains only a selected response-carrying substrate representative of each actual recorded displacement together with a positive substrate-response operator acting on that selected carrier. The current body-level forcing law is then read off as the selected substrate-response energy on the fixed displacement body.

\paragraph{Framework and claim boundary.}
\TheoryProgram{} denotes the broader \Aether{} / \Aflow{} framework built on the claims that the \Aether{} is the underlying four-dimensional substrate of reality, the \Aflow{} is its intrinsic ordered motion, observed three-dimensional space is the local experiential slice of that deeper substrate, S-time is the experienced order of change arising from matter, light, and the \Aflow{}, and observed expansion is the three-dimensional appearance of deeper four-dimensional ordered motion. Within that framework, \TheoryName{} denotes the exact-closure theory in which the effective gravitational dynamics are adopted to be exactly Einsteinian with universal matter coupling. In the active sequence, \emph{adoption} means use of that established relativistic dynamics without claiming substrate derivation, while \emph{derivation} is reserved for a first-principles recovery from explicit substrate variables.

The present note stays strictly inside that boundary. It does not claim a completed first-principles derivation of GR from final substrate microphysics. Its narrower positive role is to show that the current section-centered displacement-body quadratic forcing law is already forced once the smaller selected body-lift response package is fixed.

\section{Fixed Inputs from the Current Forcing-Law Frontier}

\begin{definition}[Recorded primitive continuation data]
\label{def:fixed}
Fix the following continuation data from the active primitive-reservoir observer-reduction line.
\begin{enumerate}
    \item For each sector label \(\sigma\in\{\Car,\Cur,\Hom\}\), a primitive forcing shell
    \[
    \ForSpace{\sigma}.
    \]
    \item The product shell
    \[
    \PrimShell
    \equiv
    \ForSpace{\Car}\times \ForSpace{\Cur}\times \ForSpace{\Hom}.
    \]
    \item The recorded metric and ordinary-matter outputs
    \[
    \MetricOut:\PrimShell\to\{\text{observer metrics}\},
    \qquad
    \MatterOut:\PrimShell\times\MatterSpace\to\{\text{observer stress tensors}\},
    \]
    satisfying
    \begin{equation}
    \MetricOut(\mathbf w)=\CompletedMetric,
    \qquad
    \MatterOut(\mathbf w,\psi)
    =
    T_{\mu\nu}^{\mathrm{matter}}[\CompletedMetric,\psi]
    \label{eq:fixedoutputs}
    \end{equation}
    for every \(\mathbf w\in\PrimShell\) and every matter configuration \(\psi\in\MatterSpace\).
\end{enumerate}
\end{definition}

\begin{definition}[Recorded benchmark base and downstream chain]
\label{def:route}
Fix \(\sigma\in\{\Car,\Cur,\Hom\}\). The active route already fixes the following data and consequences.
\begin{enumerate}
    \item the current proto-section benchmark base, in particular the recorded proto-section body \(\ProtoSectionBody{\sigma}\) and shell \(\ProtoSectionShell{\sigma}\);
    \item the fixed section-centered displacement body
    \[
    \PrePreProtoSectionResidualBody{\sigma}
    \subset
    \ProtoSectionBody{\sigma}\times\PrePreProtoSectionVertical{\sigma}
    \]
    whose fiber
    \[
    \PrePreProtoSectionResidualBody{\sigma}(y)
    \equiv
    \left\{
    v\in\PrePreProtoSectionVertical{\sigma}:(y,v)\in\PrePreProtoSectionResidualBody{\sigma}
    \right\}
    \]
    is nonempty, compact, convex, contains \(0\), and has nonempty interior for every \(y\in\ProtoSectionBody{\sigma}\);
    \item the recorded downstream continuation, namely
    \[
    \begin{aligned}
    &\PullbackBodyResponseCore,\quad
    \PullbackBodyOperatorCore,\\
    &\PullbackOperatorCore,\quad
    \PrePreProtoSectionPullbackCore,
    \end{aligned}
    \qquad
    \begin{aligned}
    &\PreProtoSectionResidualPackage,\quad
    \PreProtoSectionPackage,\\
    &\PreProtoSectionMinSectionCore,
    \end{aligned}
    \]
    together with the current continuity-Hessian compressed core and benchmark one-metric observer package;
    \item benchmark faithfulness, meaning preservation of the benchmark outputs \eqref{eq:fixedoutputs}, no second operative metric, no enlarged low-energy matter law, no change to the ordinary matter route, and no premature promotion from adoption to completed derivation.
\end{enumerate}
\end{definition}

\begin{proposition}[What the current forcing-law frontier already proves]
\label{prop:frontier}
At current scope, the already-recorded forcing-law frontier theorems prove all of the following.
\begin{enumerate}
    \item Any benchmark-faithful section-centered displacement-body quadratic forcing law canonically determines the visible-response operator family \(\VisibleResponseOperator{\sigma}\) and the canonical minimal visible-response representative \(\MinimalReducedStructure_{\sigma}\) on the fixed displacement body.
    \item Once that law is available, the current body-response core and all currently recorded downstream benchmark-facing consequences already follow unchanged from the same derived representative.
\end{enumerate}
\end{proposition}

\begin{proof}
Item (1) is exactly the content of the current theorem deriving the canonical minimal visible-response representative from the section-centered displacement-body quadratic forcing law. Item (2) is exactly the downstream factorization statement recorded there.
\end{proof}

\section{Body-Lift Response Selection}

\begin{definition}[Benchmark-faithful body-lift response selection]
\label{def:selection}
Fix \(\sigma\in\{\Car,\Cur,\Hom\}\). A \emph{benchmark-faithful body-lift response selection} for sector \(\sigma\) consists of the following data.
\begin{enumerate}
    \item The fixed proto-section benchmark base and fixed section-centered displacement body of Definition \ref{def:route}(1)--(2).
    \item A finite-dimensional Euclidean selected-lift carrier
    \[
    \LiftSelectionCarrier{\sigma}.
    \]
    \item A smooth family of linear selected response lifts
    \[
    \SelectedResponseLift{\sigma}(y):
    \PrePreProtoSectionVertical{\sigma}\to\LiftSelectionCarrier{\sigma},
    \qquad
    y\in\ProtoSectionBody{\sigma},
    \]
    used only on the recorded displacement-body fiber
    \[
    \PrePreProtoSectionResidualBody{\sigma}(y).
    \]
    \item A smooth family of positive self-adjoint selected response operators
    \[
    \SelectedResponseOperator{\sigma}(y):
    \LiftSelectionCarrier{\sigma}\to\LiftSelectionCarrier{\sigma},
    \qquad
    y\in\ProtoSectionBody{\sigma}.
    \]
    \item Positivity on the actual displacement body:
    \[
    \ev{
    \SelectedResponseLift{\sigma}(y)v,
    \SelectedResponseOperator{\sigma}(y)\SelectedResponseLift{\sigma}(y)v
    }
    =0
    \qquad\Longleftrightarrow\qquad
    v=0
    \]
    for every \(y\in\ProtoSectionBody{\sigma}\) and every \(v\in\PrePreProtoSectionResidualBody{\sigma}(y)\).
    \item Benchmark faithfulness in the sense of Definition \ref{def:route}(4).
\end{enumerate}
\end{definition}

\begin{remark}
Definition \ref{def:selection} is intentionally smaller than the older section-centered displacement-response substrate law and smaller than the later projection/body or current-image-core presentations. It retains only the explicit response-carrying selected substrate representative of each actual recorded displacement together with the positive substrate-response operator acting on that selected carrier. Ambient substrate-body points, projection/kernel decompositions, and other larger same-output presentations are not kept as separately primitive data here.
\end{remark}

\section{Forced Section-Centered Displacement-Body Quadratic Forcing Law}

\begin{definition}[Selected-lift forcing energy]
\label{def:energy}
Fix \(\sigma\in\{\Car,\Cur,\Hom\}\) and a benchmark-faithful body-lift response selection. Define the selected-lift forcing energy on the recorded displacement body by
\begin{equation}
\VisibleBodyForcingLaw{\sigma}(y,v)
\equiv
\frac{1}{2}
\ev{
\SelectedResponseLift{\sigma}(y)v,
\SelectedResponseOperator{\sigma}(y)\SelectedResponseLift{\sigma}(y)v
}
\label{eq:forcing}
\end{equation}
for every \((y,v)\in\PrePreProtoSectionResidualBody{\sigma}\).
\end{definition}

\begin{proposition}[The selected-lift forcing energy is a benchmark-faithful body-level quadratic forcing law]
\label{prop:law}
Fix a benchmark-faithful body-lift response selection for sector \(\sigma\). Then the pair
\[
\left(
\PrePreProtoSectionResidualBody{\sigma},
\VisibleBodyForcingLaw{\sigma}
\right)
\]
is a benchmark-faithful section-centered displacement-body quadratic forcing law on the fixed displacement body.
\end{proposition}

\begin{proof}
Because \(y\mapsto \SelectedResponseLift{\sigma}(y)\) and \(y\mapsto \SelectedResponseOperator{\sigma}(y)\) are smooth, the forcing energy \(\VisibleBodyForcingLaw{\sigma}\) is smooth in \(y\). Because \(v\mapsto \SelectedResponseLift{\sigma}(y)v\) is linear on \(\PrePreProtoSectionVertical{\sigma}\), the restriction of \(\VisibleBodyForcingLaw{\sigma}(y,\cdot)\) to the recorded displacement-body fiber \(\PrePreProtoSectionResidualBody{\sigma}(y)\) is quadratic in \(v\). Positivity and vanishing only at \(v=0\) on that fiber are exactly Definition \ref{def:selection}(5). Benchmark faithfulness is part of Definition \ref{def:selection}(6). Therefore the induced pair satisfies the requirements of a benchmark-faithful section-centered displacement-body quadratic forcing law on the fixed displacement body.
\end{proof}

\section{Forcing the Current Body-Law Frontier}

\begin{theorem}[Current displacement-body quadratic forcing law from body-lift response selection]
\label{thm:main}
Fix the primitive continuation data of Definition \ref{def:fixed}, the recorded benchmark base and downstream chain of Definition \ref{def:route}, and for each sector \(\sigma\in\{\Car,\Cur,\Hom\}\) a benchmark-faithful body-lift response selection in the sense of Definition \ref{def:selection}. Then the current section-centered displacement-body quadratic forcing law is canonically forced by that smaller explicit package. More precisely:
\begin{enumerate}
    \item the selected-lift forcing energy \(\VisibleBodyForcingLaw{\sigma}\) of Definition \ref{def:energy} is a benchmark-faithful section-centered displacement-body quadratic forcing law on the fixed displacement body by Proposition \ref{prop:law};
    \item by Proposition \ref{prop:frontier}(1), that law canonically determines the visible-response operator family \(\VisibleResponseOperator{\sigma}\) and the canonical minimal visible-response representative \(\MinimalReducedStructure_{\sigma}\);
    \item by Proposition \ref{prop:frontier}(2), the current body-response core and every currently recorded downstream benchmark-facing consequence in Definition \ref{def:route}(3) then follow unchanged from the same derived representative;
    \item the benchmark one-metric package \eqref{eq:fixedoutputs} is preserved, the ordinary matter route is unchanged, there is no second operative metric, and the low-energy matter law is not enlarged;
    \item consequently the remaining honest burden is no longer to restate the current section-centered displacement-body quadratic forcing law itself, but to derive or justify the smaller explicit body-lift response selection from still more primitive substrate structure.
\end{enumerate}
\end{theorem}

\begin{proof}
Item (1) is exactly Proposition \ref{prop:law}. Item (2) is Proposition \ref{prop:frontier}(1) applied to the law defined in \eqref{eq:forcing}. Item (3) is Proposition \ref{prop:frontier}(2). Item (4) is the benchmark-faithfulness condition built into Definitions \ref{def:route} and \ref{def:selection}. Item (5) is the routing consequence of Items (1)--(4): once the current body-level forcing law is itself a canonical consequence of the smaller selected body-lift response package, another manuscript that merely restates that same law or merely replays its downstream consequences does not remove any remaining benchmark-facing freedom.
\end{proof}

\begin{corollary}[The current body-level forcing law is no longer primitive]
\label{cor:nonprimitive}
Under the hypotheses of Theorem \ref{thm:main}, the current section-centered displacement-body quadratic forcing law is no longer a primitive stopping point on the recorded section-centered hidden-response route. It is a forced output of the benchmark-faithful body-lift response selection.
\end{corollary}

\begin{proof}
Theorem \ref{thm:main}(1) identifies the current body-level forcing law as the selected substrate-response energy of the smaller explicit package, while Theorem \ref{thm:main}(2)--(3) identifies the same downstream benchmark-facing consequences. The law is therefore induced rather than postulated independently.
\end{proof}

\section{Conclusion}

The positive result of this note is a genuine derivational gain below the current displacement-body forcing-law frontier. The current section-centered displacement-body quadratic forcing law is no longer primitive once the smaller body-lift response selection is fixed. The active line therefore no longer stops honestly at the body-law presentation itself.

The scope remains narrow and honest. The one operative metric is still exactly \(\CompletedMetric\), the ordinary matter route is unchanged, there is no second operative metric, the low-energy matter law is not enlarged, and nothing here upgrades adoption to a completed first-principles derivation of GR from final substrate microphysics.

The next open burden is therefore sharper again. The next benchmark-facing manuscript should derive or justify the current body-lift response selection itself from still more primitive explicit substrate structure. Another manuscript that merely restates the same selected-lift package, the same section-centered displacement-body quadratic forcing law, the same visible-response operator family, the same canonical minimal visible-response representative, or another larger same-output current-image-core or reduced-carrier or projection/body or full substrate-law presentation is no longer the clean next target at current scope.

\end{document}
