\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{geometry}
\usepackage{amsmath,amssymb,amsfonts,amsthm,mathtools}
\usepackage{bm}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{booktabs}
\usepackage{array}
\usepackage{setspace}
\usepackage{mathrsfs}
\usepackage{physics}

\geometry{margin=1in}
\hypersetup{colorlinks=true, linkcolor=black, urlcolor=blue, citecolor=black}
\setlist[enumerate]{topsep=0.4em,itemsep=0.35em}
\setlist[itemize]{topsep=0.3em,itemsep=0.25em}
\titleformat{\section}{\large\bfseries}{\thesection.}{0.5em}{}
\titleformat{\subsection}{\normalsize\bfseries}{\thesubsection.}{0.5em}{}
\setstretch{1.06}

\newcommand{\Aether}{\AE{}ther}
\newcommand{\Aflow}{\AE{}ther-flow}
\newcommand{\TheoryName}{\Aflow{} Interpretation of Relativity}
\newcommand{\TheoryProgram}{\Aether{} / \Aflow{} framework}
\newcommand{\CompletedMetric}{g^{\sharp}}

\newcommand{\CurrentBodyImageCore}{\mathfrak S^{\mathrm{disp,resp,cbimg}}}
\newcommand{\VisibleResponseOperator}{S^{\mathrm{disp,resp,vis}}}
\newcommand{\MinimalReducedStructure}{\mathfrak S^{\mathrm{disp,resp,red,min}}}

\newtheorem{definition}{Definition}
\newtheorem{proposition}{Proposition}
\newtheorem{remark}{Remark}
\newtheorem{corollary}{Corollary}
\newtheorem{theorem}{Theorem}

\title{\textbf{The \TheoryName{}}\\[0.4em]
\large Primitive-Reservoir Observer-Reduction\\
\large Section-Centered Hidden-Response\\
\large Canonical Minimal Visible-Response\\
\large Representative Necessity / Uniqueness\\
\large Next Benchmark Criterion}
\author{}
\date{}

\begin{document}

\maketitle

\begin{abstract}
The current active-primary theorem now proves that the canonical minimal visible-response representative \(\MinimalReducedStructure\) is necessary and unique at benchmark scope up to visible-response-faithful equivalence on the recorded section-centered hidden-response route. No genuinely smaller benchmark-facing datum remains there below the visible quadratic response on the fixed displacement body.

This note records the routing consequence of that gain. The next honest benchmark-facing move must now derive or justify that current visible-response datum itself from still more primitive explicit substrate structure while preserving the same benchmark one-metric package, the same ordinary matter route, and the same claim boundary. Equivalently, it must derive or justify the current positive visible-response operator \(\VisibleResponseOperator\) on the fixed displacement fibers, or derive the canonical minimal visible-response representative \(\MinimalReducedStructure\) directly from a smaller explicit substrate law without restoring the full current-image-core presentation. Another manuscript that merely restates the same visible-response datum, restores the current image-core package, re-expands to a reduced-carrier presentation, replays the older projection/body presentation, or replays the full displacement-response substrate law does not count as the clean next step. The one operative metric remains exactly \(\CompletedMetric\), there is no second operative metric, the low-energy matter law is not enlarged, and no stronger promotion language is licensed.
\end{abstract}

\section{Introduction}

The active derivational program of \TheoryName{} is no longer merely at the stage where the full canonical current-body image core should be screened out as the live burden. The new theorem spends a still sharper option below that frontier: on the recorded section-centered hidden-response route, the canonical minimal visible-response representative itself is now necessary and unique at benchmark scope up to visible-response-faithful equivalence. No smaller benchmark-facing datum remains below it there.

The present note records the routing consequence of that gain. It does not reopen the full current image-core presentation, the larger reduced-carrier presentation, the older projection-operator-core body presentation, the full displacement-response substrate law, or the larger pullback-body-operator, pullback-operator, pullback-quadratic, hidden-response, residual-normal-form, or pre-proto-section presentations as if any of those were again the live burden. It records only which kind of next manuscript would now count as an honest benchmark-facing gain below the current visible-response necessity / uniqueness frontier.

\paragraph{Framework and claim boundary.}
\TheoryProgram{} denotes the broader \Aether{} / \Aflow{} framework built on the claims that the \Aether{} is the underlying four-dimensional substrate of reality, the \Aflow{} is its intrinsic ordered motion, observed three-dimensional space is the local experiential slice of that deeper substrate, S-time is the experienced order of change arising from matter, light, and the \Aflow{}, and observed expansion is the three-dimensional appearance of deeper four-dimensional ordered motion. Within that framework, \TheoryName{} denotes the exact-closure theory in which the effective gravitational dynamics are adopted to be exactly Einsteinian with universal matter coupling. In the active sequence, \emph{adoption} means use of that established relativistic dynamics without claiming substrate derivation, while \emph{derivation} is reserved for a first-principles recovery from explicit substrate variables.

The present note stays strictly inside that boundary. It records only which kind of next manuscript would now count as an honest benchmark-facing gain below the canonical-minimal-visible-response necessity / uniqueness frontier.

\section{Fixed Inputs}

\begin{definition}[Visible-response necessity / uniqueness frontier inputs]
The criterion recorded here uses the following fixed inputs.
\begin{enumerate}
    \item The benchmark exact-closure package, which fixes the public one-metric GR target of the repository.
    \item The benchmark gatekeeping layer, including the recorded safeguard that blocks same-output deeper-origin relays from counting as new front-line progress once the live benchmark-relevant datum is unchanged.
    \item The preserved theorem chain showing that the older projection-operator-core package already collapses benchmark-facingly to the canonical minimal visible-response representative, that the later full canonical current-body image core already collapses benchmark-facingly to that same representative, and that the current active-primary theorem proves this visible-response datum is itself necessary and unique at benchmark scope up to visible-response-faithful equivalence.
    \item The recorded fact that the current body-response core and all currently recorded downstream benchmark-facing consequences already factor through the canonical minimal visible-response representative \(\MinimalReducedStructure\).
\end{enumerate}
\end{definition}

\begin{remark}
The present note does not replace those manuscripts. It records the routing consequence of reading them together under the active safeguard against recursive depth drift.
\end{remark}

\section{Why the Live Burden Now Sits Below Visible-Response Restatement}

\begin{proposition}[The live burden is renewed below visible-response restatement]
At the current stage of the primitive-reservoir observer-reduction line, the visible-response necessity / uniqueness theorem renews the live benchmark-facing burden below any mere restatement of the same canonical minimal visible-response representative \(\MinimalReducedStructure\) or of the same visible quadratic response operator \(\VisibleResponseOperator\) on the fixed displacement fibers.
\end{proposition}

\begin{proof}
That theorem changes benchmark-facing status because it proves that, on the recorded route itself, no smaller benchmark-facing datum remains below the current visible-response datum. Once that internal sharpening is in hand, another manuscript that merely renames the same visible operator, restates the same fixed displacement-body-plus-operator package, or accompanies it through another same-output realization no longer removes any remaining benchmark-facing freedom. The live burden therefore no longer sits on another visible-response restatement. It sits on deriving that visible-response datum itself from still more primitive explicit substrate structure.
\end{proof}

\begin{definition}[Benchmark-neutral same-visible-response relay below the current frontier]
A \emph{benchmark-neutral same-visible-response relay below the current frontier} is a manuscript that preserves the same benchmark one-metric output, the same ordinary matter route, the same visible-response operator \(\VisibleResponseOperator\), the same canonical minimal visible-response representative \(\MinimalReducedStructure\), the same current body-response core, and the same downstream benchmark-facing consequences while merely restating that same visible-response datum, relocating the unexplained substrate layer deeper without deriving the datum itself, restoring the already-spent full current-image-core package \(\CurrentBodyImageCore\), re-expanding to a larger reduced-carrier presentation, restoring the older projection/body presentation, replaying the full displacement-response substrate law, or otherwise carrying the same visible quadratic response through another larger same-output realization.
\end{definition}

\section{The Current Post-Uniqueness Criterion}

\begin{definition}[Admissible next benchmark-facing manuscript below the current frontier]
Below the current canonical-minimal-visible-response necessity / uniqueness frontier, a manuscript counts as an admissible next benchmark-facing move only if it does at least one of the following:
\begin{enumerate}
    \item derives or justifies the current visible-response operator \(\VisibleResponseOperator\) itself on the fixed displacement fibers from still more primitive explicit substrate structure;
    \item equivalently derives or justifies the current canonical minimal visible-response representative \(\MinimalReducedStructure\) on the fixed displacement body from still more primitive explicit substrate structure;
    \item does one of the previous two without restoring the full current-image-core presentation and while preserving the same benchmark one-metric package, the same ordinary matter route, and the same claim boundary.
\end{enumerate}
\end{definition}

\begin{theorem}[Next honest benchmark-facing task below the current frontier]
The next honest benchmark-facing manuscript below the current canonical-minimal-visible-response necessity / uniqueness frontier must derive or justify the current visible-response operator \(\VisibleResponseOperator\) on the fixed displacement fibers, equivalently the current canonical minimal visible-response representative \(\MinimalReducedStructure\) on the fixed displacement body, from still more primitive explicit substrate structure. A manuscript that only repeats the same visible-response datum through another same-output restatement, another restored current-image-core package, another larger reduced-carrier presentation, another restored projection/body package, or another replay of the full displacement-response substrate law does not satisfy the criterion.
\end{theorem}

\begin{proof}
By the preceding proposition, the live burden already lies below any mere restatement of the same visible-response datum. The present necessity / uniqueness theorem has spent the internal-sharpening option that remained inside that datum at current scope. Therefore a subsequent manuscript must improve on the visible-response datum itself rather than merely accompany it through another representation. A deeper-origin manuscript can do so only if it derives or justifies that datum from still more primitive explicit substrate structure. The remaining honest alternatives are therefore exactly those stated in the definition.
\end{proof}

\section{What the Next Move Should Not Be}

\begin{proposition}[Screened next moves below the current frontier]
Below the current canonical-minimal-visible-response necessity / uniqueness frontier, none of the following is the default next benchmark-facing move:
\begin{enumerate}
    \item another same-output deeper-origin relay that merely preserves the current visible-response operator \(\VisibleResponseOperator\) and therefore merely reproduces the same canonical minimal visible-response representative \(\MinimalReducedStructure\) together with the same current body-response core and the same downstream benchmark-facing consequences;
    \item another restoration of the full current-image-core package \(\CurrentBodyImageCore\) as if its image-body, projection / lift, or exact-shell constituents were again independently live;
    \item another restoration of a larger reduced-carrier presentation, of the older full projection/body presentation, or of the full displacement-response substrate law as if those already-spent larger packages were again the honest current burden;
    \item another replay of the larger pullback-body-operator, pullback-operator, pullback-quadratic, hidden-response, residual-normal-form, or pre-proto-section presentations as if they were again independently live below the current frontier;
    \item a manuscript that introduces a second operative metric, enlarges the ordinary matter law, or uses stronger promotion language.
\end{enumerate}
\end{proposition}

\begin{proof}
Item (1) fails the preceding criterion because it leaves the renewed live burden unchanged. Item (2) fails because it restores a realization whose benchmark-facing freedom is already screened out by the current theorem chain. Item (3) fails because it returns to larger already-spent packages rather than deriving the visible-response datum itself. Item (4) likewise re-expands to larger already-spent presentations. Item (5) violates the fixed claim boundary of the benchmark package and therefore cannot count as a disciplined next step on the active line.
\end{proof}

\begin{remark}
This screening statement is not a denial that those deeper or alternative manuscripts may matter strategically. It is a routing statement: they are not the default way to spend the next benchmark-facing move below the current frontier unless they do the same benchmark-facing work named above.
\end{remark}

\section{Conclusion}

The positive result of this note is routing discipline below the canonical-minimal-visible-response necessity / uniqueness frontier. The current theorem remains the live benchmark-facing gain because it already proves that the canonical minimal visible-response representative is necessary and unique at benchmark scope up to visible-response-faithful equivalence, so no smaller benchmark-facing datum remains below it on the recorded route. The earlier current-image-core collapse theorem remains preserved handoff history because it first moved the live burden below the full current-image-core presentation to the visible-response datum itself before the present theorem spent the remaining internal-presentational freedom there.

The scope remains narrow and honest. The benchmark package is unchanged: the one operative metric is still exactly \(\CompletedMetric\), the ordinary matter route is unchanged, there is no second operative metric, and the low-energy matter law is not enlarged. Nothing here upgrades adoption to derivation or licenses stronger promotion language.

The next open burden is therefore clear. The next benchmark-facing manuscript should derive or justify the current visible-response operator \(\VisibleResponseOperator\) on the fixed displacement fibers, equivalently derive the current canonical minimal visible-response representative \(\MinimalReducedStructure\) on the fixed displacement body, from still more primitive explicit substrate structure. Another same-visible-response restatement, another restored current-image-core package, another larger reduced-carrier replay, another restored projection/body presentation, or another replay of the full displacement-response substrate law is not the clean next manuscript target at current scope.

\end{document}
