\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{geometry}
\usepackage{amsmath,amssymb,amsfonts,amsthm,mathtools}
\usepackage{bm}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{booktabs}
\usepackage{array}
\usepackage{setspace}
\usepackage{mathrsfs}
\usepackage{physics}

\geometry{margin=1in}
\hypersetup{colorlinks=true, linkcolor=black, urlcolor=blue, citecolor=black}
\setlist[enumerate]{topsep=0.4em,itemsep=0.35em}
\setlist[itemize]{topsep=0.3em,itemsep=0.25em}
\titleformat{\section}{\large\bfseries}{\thesection.}{0.5em}{}
\titleformat{\subsection}{\normalsize\bfseries}{\thesubsection.}{0.5em}{}
\setstretch{1.06}

\newcommand{\Aether}{\AE{}ther}
\newcommand{\Aflow}{\AE{}ther-flow}
\newcommand{\TheoryName}{\Aflow{} Interpretation of Relativity}
\newcommand{\TheoryProgram}{\Aether{} / \Aflow{} framework}

\newcommand{\CompletedMetric}{g^{\sharp}}
\newcommand{\MatterSpace}{\Psi}

\newcommand{\Car}{\mathrm{car}}
\newcommand{\Cur}{\mathrm{cur}}
\newcommand{\Hom}{\mathrm{hom}}

\newcommand{\ForSpace}[1]{\mathcal I_{#1}^{\mathrm{for}}}
\newcommand{\PrimShell}{\mathcal S_{\mathrm{prim}}}
\newcommand{\MetricOut}{\mathscr G_{\mathrm{out}}}
\newcommand{\MatterOut}{\mathscr T_{\mathrm{out}}}

\newcommand{\ProtoSectionBody}[1]{\mathcal B_{#1}^{\mathrm{psec}}}
\newcommand{\ProtoSectionShell}[1]{\mathcal Z_{#1}^{\mathrm{psec}}}
\newcommand{\PrePreProtoSectionVertical}[1]{V_{#1}^{\mathrm{pppresec}}}
\newcommand{\PrePreProtoSectionResidualBody}[1]{\mathcal D_{#1}^{\mathrm{pppresec}}}

\newcommand{\PullbackBodyResponseCore}{\mathfrak S^{\mathrm{sub,proto,pppresec,pb,bodyresp}}}
\newcommand{\PullbackBodyOperatorCore}{\mathfrak S^{\mathrm{sub,proto,pppresec,pb,bodyop}}}
\newcommand{\PullbackOperatorCore}{\mathfrak S^{\mathrm{sub,proto,pppresec,pb,op}}}
\newcommand{\PrePreProtoSectionPullbackCore}{\mathfrak S^{\mathrm{sub,proto,pppresec,pb}}}
\newcommand{\PreProtoSectionResidualPackage}{\mathfrak R^{\mathrm{sub,proto,presec,res}}}
\newcommand{\PreProtoSectionPackage}{\mathfrak R^{\mathrm{sub,proto,presec}}}
\newcommand{\PreProtoSectionMinSectionCore}{\mathfrak R^{\mathrm{sub,proto,presec,sec}}}

\newcommand{\VisibleBodyForcingLaw}[1]{\mathscr F_{#1}^{\mathrm{disp,resp,vis,body}}}
\newcommand{\VisibleResponseOperator}[1]{S_{#1}^{\mathrm{disp,resp,vis}}}
\newcommand{\MinimalReducedStructure}{\mathfrak S^{\mathrm{disp,resp,red,min}}}

\newcommand{\NormalizedLiftPackage}{\widehat{\mathfrak L}^{\mathrm{disp,body,norm}}}
\newcommand{\NormalizedLiftCarrier}[1]{\widehat{\mathcal U}_{#1}^{\mathrm{disp,body,norm}}}
\newcommand{\NormalizedSelectedResponseLift}[1]{\widehat{\Lambda}_{#1}^{\mathrm{disp,body,norm}}}

\newcommand{\SquareRootOperatorCore}{\mathfrak O^{\mathrm{disp,body,sqrt}}}
\newcommand{\SquareRootOperator}[1]{R_{#1}^{\mathrm{disp,body,sqrt}}}
\newcommand{\GramOperator}[1]{G_{#1}^{\mathrm{disp,body,norm}}}

\newtheorem{definition}{Definition}
\newtheorem{proposition}{Proposition}
\newtheorem{remark}{Remark}
\newtheorem{corollary}{Corollary}
\newtheorem{theorem}{Theorem}

\title{\textbf{The \TheoryName{}}\\[0.4em]
\large Primitive-Reservoir Observer-Reduction\\
\large Section-Centered Hidden-Response\\
\large Canonical Normalized Selected-Response\\
\large Lift Collapse to a Canonical\\
\large Square-Root Operator Core}
\author{}
\date{}

\begin{document}

\maketitle

\begin{abstract}
The current active-primary theorem already proves that the current operator-bearing body-lift response selection collapses benchmark-facingly to a smaller canonical normalized selected-response lift \(\NormalizedLiftPackage\) on the fixed displacement body. The next honest benchmark-facing move is therefore no longer another replay of the selected-lift package, of the body-level forcing law, or of the visible-response structures that follow from them. It is to force the normalized selected-response lift itself, or to prove that some genuinely smaller constituent inside that normalized-lift package already carries all of its benchmark-relevant content.

The present note takes that smaller-constituent route in the cleanest available form. For each sector, a benchmark-faithful canonical normalized selected-response lift consists of a finite-dimensional Euclidean carrier and a smooth linear lift on the fixed displacement fibers. The theorem shows that this carrier-bearing package already collapses canonically to a smaller square-root operator core on the fixed displacement space:
\[
\GramOperator{\sigma}(y)
=
\NormalizedSelectedResponseLift{\sigma}(y)^*
\NormalizedSelectedResponseLift{\sigma}(y),
\qquad
\SquareRootOperator{\sigma}(y)
=
\GramOperator{\sigma}(y)^{1/2}.
\]
The current normalized-lift energy is exactly
\[
\frac{1}{2}
\ev{
\SquareRootOperator{\sigma}(y)v,
\SquareRootOperator{\sigma}(y)v
}
=
\frac{1}{2}
\ev{
v,\GramOperator{\sigma}(y)v
}
\]
on the actual displacement body. Conversely, any benchmark-faithful square-root operator core already induces a benchmark-faithful canonical normalized selected-response lift by taking the lift carrier to be the fixed displacement space itself and the lift map to be the square-root operator. Thus the separate carrier-bearing normalized-lift presentation carries no additional benchmark-facing freedom beyond the smaller square-root operator core.

The benchmark boundary remains unchanged throughout. The one operative metric is still exactly \(\CompletedMetric\), the ordinary matter route is unchanged, there is no second operative metric, the low-energy matter law is not enlarged, and no stronger promotion language is licensed. By the current forcing-law frontier, the same section-centered displacement-body quadratic forcing law, the same visible-response operator family, the same canonical minimal visible-response representative, the same current body-response core, and every currently recorded downstream benchmark-facing consequence then follow unchanged. The remaining honest burden therefore moves below the carrier-bearing normalized selected-response lift to a deeper derivation or justification of the current square-root operator core itself rather than another same-lift or same-body-law or same-operator replay.
\end{abstract}

\section{Introduction}

The active derivational program of \TheoryName{} has now already removed three larger stopping points on the recorded section-centered hidden-response route: first the visible-response operator-family presentation, then the body-level quadratic forcing law itself, and then the operator-bearing selected-lift package. The current active-primary theorem shows that once a smaller canonical normalized selected-response lift is fixed, the operator-bearing selected-lift presentation is no longer primitive.

The next honest question is therefore narrower again. Does the normalized selected-response lift itself still contain benchmark-relevant freedom, or does it already collapse to some smaller constituent? The present note answers that question in the smallest clean way presently available. It does not restore the larger selected-lift package, a larger reduced-carrier presentation, an older projection/body presentation, or a replay of the full displacement-response substrate law. Instead it shows that the carrier-bearing normalized lift already collapses to a canonical positive square-root operator acting on the fixed displacement fibers themselves. The benchmark-relevant content of the current normalized-lift package is therefore carried already by that smaller square-root operator core.

\paragraph{Framework and claim boundary.}
\TheoryProgram{} denotes the broader \Aether{} / \Aflow{} framework built on the claims that the \Aether{} is the underlying four-dimensional substrate of reality, the \Aflow{} is its intrinsic ordered motion, observed three-dimensional space is the local experiential slice of that deeper substrate, S-time is the experienced order of change arising from matter, light, and the \Aflow{}, and observed expansion is the three-dimensional appearance of deeper four-dimensional ordered motion. Within that framework, \TheoryName{} denotes the exact-closure theory in which the effective gravitational dynamics are adopted to be exactly Einsteinian with universal matter coupling. In the active sequence, \emph{adoption} means use of that established relativistic dynamics without claiming substrate derivation, while \emph{derivation} is reserved for a first-principles recovery from explicit substrate variables.

The present note stays strictly inside that boundary. It does not claim a completed first-principles derivation of GR from final substrate microphysics. Its narrower positive role is to show that the current carrier-bearing normalized selected-response lift already collapses benchmark-facingly to a smaller canonical square-root operator core on the fixed displacement fibers.

\section{Fixed Inputs from the Current Normalized-Lift Frontier}

\begin{definition}[Recorded primitive continuation data]
\label{def:fixed}
Fix the following continuation data from the active primitive-reservoir observer-reduction line.
\begin{enumerate}
    \item For each sector label \(\sigma\in\{\Car,\Cur,\Hom\}\), a primitive forcing shell
    \[
    \ForSpace{\sigma}.
    \]
    \item The product shell
    \[
    \PrimShell
    \equiv
    \ForSpace{\Car}\times \ForSpace{\Cur}\times \ForSpace{\Hom}.
    \]
    \item The recorded metric and ordinary-matter outputs
    \[
    \MetricOut:\PrimShell\to\{\text{observer metrics}\},
    \qquad
    \MatterOut:\PrimShell\times\MatterSpace\to\{\text{observer stress tensors}\},
    \]
    satisfying
    \begin{equation}
    \MetricOut(\mathbf w)=\CompletedMetric,
    \qquad
    \MatterOut(\mathbf w,\psi)
    =
    T_{\mu\nu}^{\mathrm{matter}}[\CompletedMetric,\psi]
    \label{eq:fixedoutputs}
    \end{equation}
    for every \(\mathbf w\in\PrimShell\) and every matter configuration \(\psi\in\MatterSpace\).
\end{enumerate}
\end{definition}

\begin{definition}[Recorded benchmark base and downstream chain]
\label{def:route}
Fix \(\sigma\in\{\Car,\Cur,\Hom\}\). The active route already fixes the following data and consequences.
\begin{enumerate}
    \item the current proto-section benchmark base, in particular the recorded proto-section body \(\ProtoSectionBody{\sigma}\) and shell \(\ProtoSectionShell{\sigma}\);
    \item the fixed section-centered displacement body
    \[
    \PrePreProtoSectionResidualBody{\sigma}
    \subset
    \ProtoSectionBody{\sigma}\times\PrePreProtoSectionVertical{\sigma}
    \]
    whose fiber
    \[
    \PrePreProtoSectionResidualBody{\sigma}(y)
    \equiv
    \left\{
    v\in\PrePreProtoSectionVertical{\sigma}:(y,v)\in\PrePreProtoSectionResidualBody{\sigma}
    \right\}
    \]
    is nonempty, compact, convex, contains \(0\), and has nonempty interior for every \(y\in\ProtoSectionBody{\sigma}\);
    \item the recorded downstream continuation, namely
    \[
    \begin{aligned}
    &\PullbackBodyResponseCore,\quad
    \PullbackBodyOperatorCore,\\
    &\PullbackOperatorCore,\quad
    \PrePreProtoSectionPullbackCore,
    \end{aligned}
    \qquad
    \begin{aligned}
    &\PreProtoSectionResidualPackage,\quad
    \PreProtoSectionPackage,\\
    &\PreProtoSectionMinSectionCore,
    \end{aligned}
    \]
    together with the current continuity-Hessian compressed core and benchmark one-metric observer package;
    \item benchmark faithfulness, meaning preservation of the benchmark outputs \eqref{eq:fixedoutputs}, no second operative metric, no enlarged low-energy matter law, no change to the ordinary matter route, and no premature promotion from adoption to completed derivation.
\end{enumerate}
\end{definition}

\begin{proposition}[What the current normalized-lift frontier already proves]
\label{prop:frontier}
At current scope, the already-recorded normalized-lift frontier theorems prove all of the following.
\begin{enumerate}
    \item Any benchmark-faithful canonical normalized selected-response lift canonically determines the current section-centered displacement-body quadratic forcing law on the fixed displacement body.
    \item That law canonically determines the visible-response operator family \(\VisibleResponseOperator{\sigma}\) and the canonical minimal visible-response representative \(\MinimalReducedStructure_{\sigma}\).
    \item The current body-response core and every currently recorded downstream benchmark-facing consequence then follow unchanged from the same derived representative.
\end{enumerate}
\end{proposition}

\begin{proof}
Item (1) is exactly the content of the current body-lift-response-selection collapse theorem once the operator-bearing presentation has been reduced to the normalized lift. Items (2) and (3) are exactly the earlier forcing-law downstream continuation already preserved on the recorded route.
\end{proof}

\section{Canonical Normalized Selected-Response Lift}

\begin{definition}[Benchmark-faithful canonical normalized selected-response lift]
\label{def:normalized}
Fix \(\sigma\in\{\Car,\Cur,\Hom\}\). A \emph{benchmark-faithful canonical normalized selected-response lift} for sector \(\sigma\) consists of the following data.
\begin{enumerate}
    \item The fixed proto-section benchmark base and fixed section-centered displacement body of Definition \ref{def:route}(1)--(2).
    \item A finite-dimensional Euclidean normalized selected-response carrier
    \[
    \NormalizedLiftCarrier{\sigma}.
    \]
    \item A smooth family of linear normalized selected-response lifts
    \[
    \NormalizedSelectedResponseLift{\sigma}(y):
    \PrePreProtoSectionVertical{\sigma}\to\NormalizedLiftCarrier{\sigma},
    \qquad
    y\in\ProtoSectionBody{\sigma},
    \]
    used only on the recorded displacement-body fiber
    \[
    \PrePreProtoSectionResidualBody{\sigma}(y).
    \]
    \item Positivity on the actual displacement body:
    \[
    \ev{
    \NormalizedSelectedResponseLift{\sigma}(y)v,
    \NormalizedSelectedResponseLift{\sigma}(y)v
    }
    =0
    \qquad\Longleftrightarrow\qquad
    v=0
    \]
    for every \(y\in\ProtoSectionBody{\sigma}\) and every \(v\in\PrePreProtoSectionResidualBody{\sigma}(y)\).
    \item Benchmark faithfulness in the sense of Definition \ref{def:route}(4).
\end{enumerate}
\end{definition}

\begin{remark}
Definition \ref{def:normalized} is already smaller than the earlier operator-bearing selected-lift presentation. The question addressed here is whether even this carrier-bearing normalized-lift package still contains benchmark-relevant freedom once the actual displacement body is fixed.
\end{remark}

\section{Canonical Square-Root Operator Core}

\begin{definition}[Benchmark-faithful canonical square-root operator core]
\label{def:sqrtcore}
Fix \(\sigma\in\{\Car,\Cur,\Hom\}\). A \emph{benchmark-faithful canonical square-root operator core} for sector \(\sigma\) consists of the following data.
\begin{enumerate}
    \item The fixed proto-section benchmark base and fixed section-centered displacement body of Definition \ref{def:route}(1)--(2).
    \item A smooth family of positive self-adjoint square-root operators
    \[
    \SquareRootOperator{\sigma}(y):
    \PrePreProtoSectionVertical{\sigma}\to\PrePreProtoSectionVertical{\sigma},
    \qquad
    y\in\ProtoSectionBody{\sigma}.
    \]
    \item Positivity on the actual displacement body:
    \[
    \ev{
    \SquareRootOperator{\sigma}(y)v,
    \SquareRootOperator{\sigma}(y)v
    }
    =0
    \qquad\Longleftrightarrow\qquad
    v=0
    \]
    for every \(y\in\ProtoSectionBody{\sigma}\) and every \(v\in\PrePreProtoSectionResidualBody{\sigma}(y)\).
    \item Benchmark faithfulness in the sense of Definition \ref{def:route}(4).
\end{enumerate}
\end{definition}

\begin{remark}
Definition \ref{def:sqrtcore} is strictly smaller than Definition \ref{def:normalized}. It retains only a positive operator acting on the fixed displacement space itself. The extra carrier of the normalized-lift presentation, together with any remaining postcomposition freedom in that carrier, is no longer treated as independently primitive data here.
\end{remark}

\begin{proposition}[A normalized selected-response lift determines a canonical square-root operator core]
\label{prop:sqrt}
Fix a benchmark-faithful canonical normalized selected-response lift for sector \(\sigma\). Define
\begin{equation}
\GramOperator{\sigma}(y)
\equiv
\NormalizedSelectedResponseLift{\sigma}(y)^*
\NormalizedSelectedResponseLift{\sigma}(y),
\qquad
\SquareRootOperator{\sigma}(y)
\equiv
\GramOperator{\sigma}(y)^{1/2}
\label{eq:sqrtcore}
\end{equation}
for each \(y\in\ProtoSectionBody{\sigma}\). Then \(\SquareRootOperator{\sigma}\) is a benchmark-faithful canonical square-root operator core.
\end{proposition}

\begin{proof}
For each \(y\in\ProtoSectionBody{\sigma}\), the operator
\[
\GramOperator{\sigma}(y)
=
\NormalizedSelectedResponseLift{\sigma}(y)^*
\NormalizedSelectedResponseLift{\sigma}(y)
\]
is positive and self-adjoint on the finite-dimensional Euclidean space \(\PrePreProtoSectionVertical{\sigma}\). It therefore has a unique positive self-adjoint square root \(\SquareRootOperator{\sigma}(y)\). Smooth dependence on \(y\) follows from the smooth dependence of the lift family and the smooth functional calculus for positive operators in finite dimension.

For \((y,v)\in\PrePreProtoSectionResidualBody{\sigma}\),
\[
\ev{
\SquareRootOperator{\sigma}(y)v,
\SquareRootOperator{\sigma}(y)v
}
=
\ev{
v,\GramOperator{\sigma}(y)v
}
=
\ev{
\NormalizedSelectedResponseLift{\sigma}(y)v,
\NormalizedSelectedResponseLift{\sigma}(y)v
}.
\]
Hence positivity and vanishing only at \(v=0\) on the actual displacement body are exactly Definition \ref{def:normalized}(4). Benchmark faithfulness is inherited from Definition \ref{def:normalized}(5). Therefore the data satisfy Definition \ref{def:sqrtcore}.
\end{proof}

\begin{proposition}[A square-root operator core induces a canonical normalized selected-response lift]
\label{prop:lift}
Fix a benchmark-faithful canonical square-root operator core for sector \(\sigma\). Then the data
\[
\NormalizedLiftCarrier{\sigma}
\equiv
\PrePreProtoSectionVertical{\sigma},
\qquad
\NormalizedSelectedResponseLift{\sigma}(y)
\equiv
\SquareRootOperator{\sigma}(y)
\]
form a benchmark-faithful canonical normalized selected-response lift.
\end{proposition}

\begin{proof}
Smoothness and linearity are immediate. Positivity on the actual displacement body becomes exactly
\[
\ev{
\NormalizedSelectedResponseLift{\sigma}(y)v,
\NormalizedSelectedResponseLift{\sigma}(y)v
}
=
\ev{
\SquareRootOperator{\sigma}(y)v,
\SquareRootOperator{\sigma}(y)v
},
\]
which is positive and vanishes only at \(v=0\) by Definition \ref{def:sqrtcore}(3). Benchmark faithfulness is inherited from Definition \ref{def:sqrtcore}(4). Therefore the induced data satisfy Definition \ref{def:normalized}.
\end{proof}

\begin{definition}[Square-root operator-core forcing energy]
\label{def:energy}
Fix \(\sigma\in\{\Car,\Cur,\Hom\}\) and a benchmark-faithful canonical square-root operator core. Define the square-root-operator-core forcing energy on the recorded displacement body by
\begin{equation}
\VisibleBodyForcingLaw{\sigma}(y,v)
\equiv
\frac{1}{2}
\ev{
\SquareRootOperator{\sigma}(y)v,
\SquareRootOperator{\sigma}(y)v
}
\label{eq:forcing}
\end{equation}
for every \((y,v)\in\PrePreProtoSectionResidualBody{\sigma}\).
\end{definition}

\begin{proposition}[The square-root operator-core energy agrees with the normalized-lift energy]
\label{prop:energy}
Fix a benchmark-faithful canonical normalized selected-response lift and let \(\SquareRootOperator{\sigma}\) be its associated square-root operator core from Proposition \ref{prop:sqrt}. Then for every \((y,v)\in\PrePreProtoSectionResidualBody{\sigma}\),
\[
\frac{1}{2}
\ev{
\SquareRootOperator{\sigma}(y)v,
\SquareRootOperator{\sigma}(y)v
}
=
\frac{1}{2}
\ev{
\NormalizedSelectedResponseLift{\sigma}(y)v,
\NormalizedSelectedResponseLift{\sigma}(y)v
}
=
\frac{1}{2}
\ev{
v,\GramOperator{\sigma}(y)v
}.
\]
Hence the current body-level forcing law determined from the normalized-lift package is exactly the square-root-operator-core energy \eqref{eq:forcing}.
\end{proposition}

\begin{proof}
This is exactly the identity proved in Proposition \ref{prop:sqrt}. The first equality is
\[
\ev{
\SquareRootOperator{\sigma}(y)v,
\SquareRootOperator{\sigma}(y)v
}
=
\ev{
v,\SquareRootOperator{\sigma}(y)^2v
}
=
\ev{
v,\GramOperator{\sigma}(y)v
},
\]
while the second equality follows from the definition of \(\GramOperator{\sigma}(y)\).
\end{proof}

\begin{proposition}[The square-root operator core squares to the current visible-response operator family]
\label{prop:visible}
Fix a benchmark-faithful canonical normalized selected-response lift for sector \(\sigma\), let \(\SquareRootOperator{\sigma}\) be its associated square-root operator core from Proposition \ref{prop:sqrt}, and let \(\VisibleResponseOperator{\sigma}\) be the unique visible-response operator family attached to the induced forcing law by Proposition \ref{prop:frontier}(2). Then
\[
\VisibleResponseOperator{\sigma}(y)
=
\SquareRootOperator{\sigma}(y)^2
=
\GramOperator{\sigma}(y)
=
\NormalizedSelectedResponseLift{\sigma}(y)^*
\NormalizedSelectedResponseLift{\sigma}(y)
\]
for every \(y\in\ProtoSectionBody{\sigma}\).
\end{proposition}

\begin{proof}
By Proposition \ref{prop:energy},
\[
\frac{1}{2}
\ev{
\SquareRootOperator{\sigma}(y)v,
\SquareRootOperator{\sigma}(y)v
}
=
\frac{1}{2}
\ev{
\NormalizedSelectedResponseLift{\sigma}(y)v,
\NormalizedSelectedResponseLift{\sigma}(y)v
}
\]
for every \(v\in\PrePreProtoSectionResidualBody{\sigma}(y)\). By Proposition \ref{prop:frontier}(2), the same forcing law is also
\[
\frac{1}{2}
\ev{
v,\VisibleResponseOperator{\sigma}(y)v
}
\]
on that same fiber. Therefore the quadratic forms of \(\VisibleResponseOperator{\sigma}(y)\) and \(\SquareRootOperator{\sigma}(y)^2=\GramOperator{\sigma}(y)\) agree on the compact convex fiber \(\PrePreProtoSectionResidualBody{\sigma}(y)\), which contains \(0\) and has nonempty interior in \(\PrePreProtoSectionVertical{\sigma}\). Two quadratic forms that agree on such a set agree on the whole vector space. Hence their representing self-adjoint operators are equal.
\end{proof}

\section{Collapsing the Current Normalized-Lift Frontier}

\begin{theorem}[Current canonical normalized selected-response lift collapses to a canonical square-root operator core]
\label{thm:main}
Fix the primitive continuation data of Definition \ref{def:fixed}, the recorded benchmark base and downstream chain of Definition \ref{def:route}, and for each sector \(\sigma\in\{\Car,\Cur,\Hom\}\) a benchmark-faithful canonical normalized selected-response lift in the sense of Definition \ref{def:normalized}. Then the current carrier-bearing normalized-lift package carries no additional benchmark-facing freedom beyond a smaller canonical square-root operator core. More precisely:
\begin{enumerate}
    \item Proposition \ref{prop:sqrt} canonically associates to the given normalized lift a benchmark-faithful square-root operator core \(\SquareRootOperator{\sigma}\).
    \item Proposition \ref{prop:lift} recovers from that square-root operator core a benchmark-faithful canonical normalized selected-response lift with carrier equal to the fixed displacement space itself, so the separate carrier-bearing presentation is not independently primitive at current benchmark scope.
    \item By Proposition \ref{prop:energy}, the current section-centered displacement-body quadratic forcing law is exactly the square-root-operator-core energy \eqref{eq:forcing}.
    \item By Proposition \ref{prop:visible}, the square-root operator core squares to the same visible-response operator family \(\VisibleResponseOperator{\sigma}\) already fixed by the forcing-law frontier.
    \item By Proposition \ref{prop:frontier}(2)--(3), the same canonical minimal visible-response representative \(\MinimalReducedStructure_{\sigma}\), the same current body-response core, and every currently recorded downstream benchmark-facing consequence then follow unchanged from that same square-root-operator-core energy.
    \item The benchmark one-metric package \eqref{eq:fixedoutputs} is preserved, the ordinary matter route is unchanged, there is no second operative metric, and the low-energy matter law is not enlarged.
    \item Consequently the remaining honest burden is no longer to restate the carrier-bearing normalized selected-response lift itself, but to derive or justify the smaller square-root operator core from still more primitive substrate structure.
\end{enumerate}
\end{theorem}

\begin{proof}
Item (1) is Proposition \ref{prop:sqrt}. Item (2) is Proposition \ref{prop:lift}. Item (3) is Proposition \ref{prop:energy}. Item (4) is Proposition \ref{prop:visible}. Item (5) is exactly the previously recorded downstream continuation applied to the forcing law \eqref{eq:forcing}. Item (6) is the benchmark-faithfulness condition built into Definitions \ref{def:route}, \ref{def:normalized}, and \ref{def:sqrtcore}. Item (7) is the routing consequence of Items (1)--(6): once the current normalized-lift package collapses benchmark-facingly to the smaller square-root operator core, another manuscript that merely restates the same carrier-bearing normalized lift or merely replays the same body-law or visible-response consequences does not remove any remaining benchmark-facing freedom.
\end{proof}

\begin{corollary}[The carrier-bearing normalized-lift presentation is no longer primitive]
\label{cor:nonprimitive}
Under the hypotheses of Theorem \ref{thm:main}, the current carrier-bearing canonical normalized selected-response lift is no longer a primitive stopping point on the recorded section-centered hidden-response route. Its benchmark-relevant content is already carried by the smaller canonical square-root operator core.
\end{corollary}

\begin{proof}
Theorem \ref{thm:main}(1)--(3) identifies the same forcing law as the square-root-operator-core energy, while Theorem \ref{thm:main}(4)--(5) identifies the same visible-response and downstream benchmark-facing consequences. Therefore the separate carrier-bearing normalized-lift presentation is dispensable at current benchmark scope.
\end{proof}

\section{Conclusion}

The positive result of this note is a genuine internal sharpening below the current normalized selected-response-lift frontier. The present carrier-bearing normalized selected-response lift no longer needs to be treated as a separately primitive package. Its benchmark-relevant content already collapses to a smaller canonical square-root operator core on the fixed displacement fibers.

The scope remains narrow and honest. The one operative metric is still exactly \(\CompletedMetric\), the ordinary matter route is unchanged, there is no second operative metric, the low-energy matter law is not enlarged, and nothing here upgrades adoption to a completed first-principles derivation of GR from final substrate microphysics.

The next open burden is therefore sharper again. The next benchmark-facing manuscript should derive or justify the current square-root operator core itself from still more primitive explicit substrate structure. Another manuscript that merely restates the same carrier-bearing normalized selected-response lift, the same operator-bearing selected-lift package, the same section-centered displacement-body quadratic forcing law, the same visible-response operator family, the same canonical minimal visible-response representative, or a larger same-output current-image-core or reduced-carrier or projection/body or full substrate-law presentation is no longer the clean next target at current scope.

\end{document}
