\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{geometry}
\usepackage{amsmath,amssymb,amsfonts,amsthm,mathtools}
\usepackage{bm}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{booktabs}
\usepackage{array}
\usepackage{setspace}
\usepackage{mathrsfs}
\usepackage{physics}

\geometry{margin=1in}
\hypersetup{colorlinks=true, linkcolor=black, urlcolor=blue, citecolor=black}
\setlist[enumerate]{topsep=0.4em,itemsep=0.35em}
\setlist[itemize]{topsep=0.3em,itemsep=0.25em}
\titleformat{\section}{\large\bfseries}{\thesection.}{0.5em}{}
\titleformat{\subsection}{\normalsize\bfseries}{\thesubsection.}{0.5em}{}
\setstretch{1.06}

\newcommand{\Aether}{\AE{}ther}
\newcommand{\Aflow}{\AE{}ther-flow}
\newcommand{\TheoryName}{\Aflow{} Interpretation of Relativity}
\newcommand{\TheoryProgram}{\Aether{} / \Aflow{} framework}
\newcommand{\CompletedMetric}{g^{\sharp}}

\newcommand{\ProjectionOperatorCore}{\mathfrak S^{\mathrm{disp,resp,projop}}}
\newcommand{\MinimalReducedStructure}{\mathfrak S^{\mathrm{disp,resp,red,min}}}
\newcommand{\VisibleResponseOperator}{S^{\mathrm{disp,resp,vis}}}

\newtheorem{definition}{Definition}
\newtheorem{proposition}{Proposition}
\newtheorem{remark}{Remark}
\newtheorem{corollary}{Corollary}
\newtheorem{theorem}{Theorem}

\title{\textbf{The \TheoryName{}}\\[0.4em]
\large Primitive-Reservoir Observer-Reduction\\
\large Section-Centered Hidden-Response\\
\large Projection-Operator Core Collapse to\\
\large Canonical Minimal Visible-Response Representative\\
\large Next Benchmark Criterion}
\author{}
\date{}

\begin{document}

\maketitle

\begin{abstract}
The current active-primary theorem now proves that a benchmark-faithful current-body-realizing section-centered hidden-response projection-operator core \(\ProjectionOperatorCore\) already determines a unique positive visible-response operator \(\VisibleResponseOperator\) on the fixed section-centered displacement fibers and therefore collapses benchmark-facingly to the canonical minimal visible-response representative \(\MinimalReducedStructure\). The full substrate-body presentation, any larger reduced carrier presentation, and all inert kernel directions are no longer independently live benchmark-facing burdens there.

This note records the routing consequence of that gain. The next honest benchmark-facing move must now derive or justify the canonical minimal visible-response representative \(\MinimalReducedStructure\) itself, equivalently the visible quadratic response operator \(\VisibleResponseOperator\) on the fixed displacement fibers, from still more primitive explicit substrate structure while preserving the same benchmark one-metric package, the same ordinary matter route, and the same claim boundary. Another manuscript that merely re-adjoins inert kernel directions, restores a larger reduced carrier presentation, replays the projection-operator core, or replays the full displacement-response substrate law does not count as the clean next step. The one operative metric remains exactly \(\CompletedMetric\), there is no second operative metric, the low-energy matter law is not enlarged, and no stronger promotion language is licensed.
\end{abstract}

\section{Introduction}

The active derivational program of \TheoryName{} is no longer merely at reduced-structure necessity / uniqueness scope on the section-centered hidden-response line. The new theorem already spends the equivalence route that the prior routing note left open: from the older explicit projection-operator-core package it canonically extracts the minimal visible-response representative itself. What remains live is no longer the carrier-level reduced structure, the full projection/body presentation, or any inert kernel extension. It is the visible quadratic response on the fixed displacement fibers.

The present note records the routing consequence of that gain. It does not reopen the larger projection-operator-core presentation, the full displacement-response substrate law, the larger pullback-body-operator, pullback-operator, pullback-quadratic, hidden-response, residual-normal-form, or pre-proto-section presentations, or another compatible carrier expansion as if any of those were again the live burden. It records only which kind of next manuscript would now count as an honest benchmark-facing gain below the new visible-response frontier.

\paragraph{Framework and claim boundary.}
\TheoryProgram{} denotes the broader \Aether{} / \Aflow{} framework built on the claims that the \Aether{} is the underlying four-dimensional substrate of reality, the \Aflow{} is its intrinsic ordered motion, observed three-dimensional space is the local experiential slice of that deeper substrate, S-time is the experienced order of change arising from matter, light, and the \Aflow{}, and observed expansion is the three-dimensional appearance of deeper four-dimensional ordered motion. Within that framework, \TheoryName{} denotes the exact-closure theory in which the effective gravitational dynamics are adopted to be exactly Einsteinian with universal matter coupling. In the active sequence, \emph{adoption} means use of that established relativistic dynamics without claiming substrate derivation, while \emph{derivation} is reserved for a first-principles recovery from explicit substrate variables.

The present note stays strictly inside that boundary. It records only which kind of next manuscript would now count as an honest benchmark-facing gain below the canonical minimal visible-response frontier.

\section{Fixed Inputs}

\begin{definition}[Visible-response frontier inputs]
The criterion recorded here uses the following fixed inputs.
\begin{enumerate}
    \item The benchmark exact-closure package, which fixes the public one-metric GR target of the repository.
    \item The benchmark gatekeeping layer, including the recorded safeguard that blocks same-output deeper-origin relays from counting as new front-line progress once the live benchmark-relevant datum is unchanged.
    \item The preserved theorem chain showing that the full canonical current-body image core is forced once a reduced projection-response substrate structure is fixed, and that any compatible reduced structure is itself unavoidable up to inert kernel extension once the fixed current image core is held fixed.
    \item The new theorem proving that the older projection-operator-core package already collapses benchmark-facingly to the canonical minimal visible-response representative \(\MinimalReducedStructure\), equivalently to the visible quadratic response operator \(\VisibleResponseOperator\) on the fixed displacement fibers.
\end{enumerate}
\end{definition}

\begin{remark}
The present note does not replace those manuscripts. It records the routing consequence of reading them together under the active safeguard against recursive depth drift.
\end{remark}

\section{Why the Live Burden Now Sits Below Visible-Response Restatement}

\begin{proposition}[The live burden is renewed below visible-response restatement]
At the current stage of the primitive-reservoir observer-reduction line, the visible-response-collapse theorem renews the live benchmark-facing burden below any mere restatement of the same canonical minimal visible-response representative \(\MinimalReducedStructure\) or of the same visible quadratic response operator \(\VisibleResponseOperator\) on the fixed displacement fibers.
\end{proposition}

\begin{proof}
That theorem changes benchmark-facing status because it proves that the older explicit projection-operator-core package already carries no benchmark-facing content beyond the visible quadratic response representative on the fixed displacement fibers. Once that collapse is in hand, another manuscript that merely re-adjoins kernel directions, restores a larger carrier presentation, renames the same visible operator, or replays the same projection/body package no longer removes any remaining benchmark-facing freedom. The live burden therefore no longer sits on another representation of the same visible-response datum. It sits on deriving that visible-response representative itself from still more primitive explicit substrate structure.
\end{proof}

\begin{definition}[Benchmark-neutral same-visible-response relay below the current frontier]
A \emph{benchmark-neutral same-visible-response relay below the current frontier} is a manuscript that preserves the same benchmark one-metric output, the same ordinary matter route, the same canonical minimal visible-response representative \(\MinimalReducedStructure\), the same visible quadratic response operator \(\VisibleResponseOperator\), and the same downstream benchmark-facing consequences while merely adjoining or removing inert kernel directions, restoring a larger reduced carrier presentation, restoring the already-screened projection-operator-core body presentation, replaying the full displacement-response substrate law, or re-expanding back to the larger pullback-body-operator, pullback-operator, pullback-quadratic, hidden-response, residual-normal-form, or pre-proto-section presentations without a new derivation of the visible-response representative itself.
\end{definition}

\section{The Current Post-Visible-Response Criterion}

\begin{definition}[Admissible next benchmark-facing manuscript below the current frontier]
Below the current canonical-minimal-visible-response frontier, a manuscript counts as an admissible next benchmark-facing move only if it does at least one of the following:
\begin{enumerate}
    \item derives or justifies the canonical minimal visible-response representative \(\MinimalReducedStructure\) itself from still more primitive explicit substrate structure;
    \item equivalently derives or justifies the visible quadratic response operator \(\VisibleResponseOperator\) on the fixed displacement fibers from still more primitive explicit substrate structure;
    \item proves a sharper necessity, uniqueness, or compatibility theorem strictly inside that visible-response representative while preserving the same benchmark one-metric package, the same ordinary matter route, and the same claim boundary.
\end{enumerate}
\end{definition}

\begin{theorem}[Next honest benchmark-facing task below the current frontier]
The next honest benchmark-facing manuscript below the current canonical-minimal-visible-response frontier must derive or justify the canonical minimal visible-response representative \(\MinimalReducedStructure\), equivalently the visible quadratic response operator \(\VisibleResponseOperator\) on the fixed displacement fibers, from still more primitive explicit substrate structure, or prove a still sharper theorem strictly inside that visible representative. A manuscript that only repeats the same visible-response datum through another larger carrier presentation, merely re-adjoins inert kernel directions, restores the projection-operator core, replays the full displacement-response substrate law, or re-expands the discussion back to larger already-spent presentations does not satisfy the criterion.
\end{theorem}

\begin{proof}
By the preceding proposition, the live burden already lies below any mere restatement of the same visible-response representative. Therefore a subsequent manuscript must improve on that now-forced visible datum rather than merely accompany it through another same-output presentation. A deeper-origin manuscript can do so only if it changes benchmark-facing status by more than representation alone. The remaining honest alternatives are therefore exactly those stated in the definition.
\end{proof}

\section{What the Next Move Should Not Be}

\begin{proposition}[Screened next moves below the current frontier]
Below the current canonical-minimal-visible-response frontier, none of the following is the default next benchmark-facing move:
\begin{enumerate}
    \item another same-output deeper-origin relay that merely preserves the current visible quadratic response operator \(\VisibleResponseOperator\) and therefore merely reproduces the same canonical minimal visible-response representative \(\MinimalReducedStructure\) together with the same downstream benchmark-facing consequences;
    \item another restoration of a larger reduced carrier presentation or of the older full projection-operator-core body presentation as if that already-screened larger freedom were again independently live;
    \item another replay of the full displacement-response substrate law or the larger pullback-body-operator, pullback-operator, pullback-quadratic, hidden-response, residual-normal-form, or pre-proto-section presentations as if those already-spent larger presentations were again the honest current burden;
    \item a manuscript that introduces a second operative metric, enlarges the ordinary matter law, or uses stronger promotion language.
\end{enumerate}
\end{proposition}

\begin{proof}
Item (1) fails the preceding criterion because it leaves the renewed live burden unchanged. Item (2) likewise fails because it restores a larger presentation whose benchmark-facing freedom is already screened out. Item (3) fails because it re-expands to larger already-spent presentations rather than deriving the visible-response representative itself. Item (4) violates the fixed claim boundary of the benchmark package and therefore cannot count as a disciplined next step on the active line.
\end{proof}

\begin{remark}
This screening statement is not a denial that those deeper or alternative manuscripts may matter strategically. It is a routing statement: they are not the default way to spend the next benchmark-facing move below the current frontier unless they do the same benchmark-facing work named above.
\end{remark}

\section{Conclusion}

The positive result of this note is routing discipline below the canonical-minimal-visible-response frontier. The present theorem remains the live benchmark-facing gain because it already proves that the older projection-operator-core package carries no benchmark-facing content beyond the visible quadratic response on the fixed displacement fibers. The earlier reduced-structure necessity / uniqueness theorem remains preserved handoff history because it first showed that carrier-level reduced-structure alternatives were unavoidable up to inert kernel extension before the present theorem collapsed the older explicit package all the way to the visible representative itself.

The scope remains narrow and honest. The benchmark package is unchanged: the one operative metric is still exactly \(\CompletedMetric\), the ordinary matter route is unchanged, there is no second operative metric, and the low-energy matter law is not enlarged. Nothing here upgrades adoption to derivation or licenses stronger promotion language.

The next open burden is therefore clear. The next benchmark-facing manuscript should derive or justify the canonical minimal visible-response representative \(\MinimalReducedStructure\) itself, equivalently derive the visible quadratic response operator \(\VisibleResponseOperator\) on the fixed displacement fibers, from still more primitive explicit substrate structure. Another same-output kernel-extension relay, another restored reduced carrier presentation, another restoration of the projection-operator core, or another replay of the full displacement-response substrate law is not the clean next manuscript target at current scope.

\end{document}
