\begingroup
\setlength{\fboxsep}{8pt}
\begin{center}
\fbox{%
\begin{minipage}{0.94\textwidth}
\small
\textbf{What This Package Is Not.}
For first-time readers, the comparison boundary is deliberately blunt.
\begin{itemize}[leftmargin=1.5em,itemsep=0.15em,topsep=0.3em,parsep=0pt,partopsep=0pt]
    \item \textbf{Not Einstein-aether theory.} The benchmark package does not add a dynamical preferred-frame vector field in the low-energy action; the congruence / \Aflow{} layer is a kinematical GR dictionary inside the adopted metric spacetime.
    \item \textbf{Not Ho\v{r}ava or preferred-foliation gravity.} The active package does not claim a preferred slicing, modified low-energy symmetry structure, or an extra low-energy foliation sector.
    \item \textbf{Not a low-energy alternative to GR.} At observable scale the package is ordinary GR with one operative metric and universal matter coupling.
    \item \textbf{Not an already completed emergent-gravity derivation.} The package does not claim that Einsteinian observer dynamics have already been recovered from explicit substrate microphysics or uniquely forced from a substrate action.
    \item \textbf{Not the downstream frozen-line obstruction note.} The current-line no-go is a separate status result on a frozen primitive-reservoir bridge object; it does not define the benchmark package itself.
\end{itemize}
\textit{Positive mirror.} The benchmark package is the public result now: an exact-GR theory statement already fixed at observable scale, with the frozen-line no-go kept separate as downstream status and any future derivational restart requiring genuinely new observer-localizing structure.
\end{minipage}%
}
\end{center}
\endgroup
